---
title: "N4 Connect Longitudinal Summaries"
date: '`r format(Sys.time(), "%B %d, %Y %r %Z")`'
date-format: MMMM D, YYYY h:mm A z
format: 
  html:
    theme: flatly
    page-layout: full
    embed-resources: true
    toc: true
    toc_float: 
    collapsed: false
    toc_depth: 5
editor: source
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, comment=NA, fig.width = 3, fig.asp = 0.618, out.width = "100%", fig.align = "center", dev='svg')
```

```{r, results='hide'}
library(openxlsx)
library(tidyverse)
library(table1)
library(REDCapTidieR)
library(labelled)
library(data.table)
library(kableExtra)
library(pander)
library(ggconsort)
library(flextable)

panderOptions('table.split.table', Inf)
# gdtools::register_gfont()
set_flextable_defaults(font.size = 12)
```


```{r}
# Import N4 project data from REDCap
options(redcaptidier.allow.mixed.structure = TRUE)

tkns <- openxlsx::read.xlsx("tokens.xlsx")
uri <- "https://redcap.nyu.edu/api/"
token <- tkns[2,2]
```

```{r}
N4_meta <- REDCapR::redcap_metadata_read(redcap_uri=uri, token=token)
```

```{r, results='hide'}
N4_meta[["success"]]
N4_meta[["data"]] |> subset(, select = "form_name") |> unique() |> as.vector()
```

```{r}
save(list = "N4_meta", file = "N4-Meta.RData")
```

```{r}
# > unique(meta_DT$form)
#  [1] "unique_id"                     "screener_1"                    "screen_2_consent"             
#  [4] "screener_2"                    "locator_form"                  "zoom_tracker_form"            
#  [7] "study_optout_form"             "blood_draw_form"               "lab_upload_form"              
# [10] "drug_test_form"                "baseline_consent_form"         "baseline_interview_editing"   
# [13] "referral_form"                 "follow_up_1_interview_editing" "follow_up_2_interview"        
# [16] "fu1_referral_form_staff"       "ema_form"                      "ema_burst_1_form"             
# [19] "ema_burst_2_form"              "ema_burst_3_form"              "ema_burst_4_form"             
# [22] "ema_burst_5_form"              "ema_burst_6_form"              "ema_burst_7_form"             
# [25] "ema_burst_8_form"              "practice_ema"                  "ema_daily_assessment"         
# [28] "ema_end_of_day_assessment"     "qi_interviews"                 "ema_optout_form_staff"        
# [31] "study_withdrawal_form" 
```

```{r}
N4_screen_stbl <- read_redcap(redcap_uri=uri, forms = c("screener_1",
                                                        "screen_2_consent",
                                                        "screener_2",
                                                        "study_withdrawal_form"), 
                       raw_or_label = "haven", token=token,
                       allow_mixed_structure = TRUE)

N4_bl_stbl <- read_redcap(redcap_uri=uri, forms = c("baseline_interview_editing"), 
                       raw_or_label = "haven", token=token,
                       allow_mixed_structure = TRUE)

N4_fu1_stbl <- read_redcap(redcap_uri=uri, forms = c("follow_up_1_interview_editing"), 
                       raw_or_label = "haven", token=token,
                       allow_mixed_structure = TRUE)

N4_fu2_stbl <- read_redcap(redcap_uri=uri, forms = c("follow_up_2_interview"), 
                       raw_or_label = "haven", token=token,
                       allow_mixed_structure = TRUE)

N4_ema_stbl <- read_redcap(redcap_uri=uri, forms = c("ema_form",
                                                     "ema_burst_1_form",
                                                     "ema_burst_2_form",
                                                     "ema_burst_3_form",
                                                     "ema_burst_4_form",
                                                     "ema_burst_5_form",
                                                     "ema_burst_6_form",
                                                     "ema_burst_7_form",
                                                     "ema_burst_8_form",
                                                     "ema_daily_assessment",
                                                     "ema_end_of_day_assessment",
                                                     "ema_optout_form_staff"), 
                       raw_or_label = "haven", token=token,
                       allow_mixed_structure = TRUE)

N4_blood_stbl <- read_redcap(redcap_uri=uri, forms = c("blood_draw_form"), 
                       raw_or_label = "haven", token=token,
                       allow_mixed_structure = TRUE)

N4_drug_stbl <- read_redcap(redcap_uri=uri, forms = c("drug_test_form"), 
                       raw_or_label = "haven", token=token,
                       allow_mixed_structure = TRUE)

N4_loc_stbl <- read_redcap(redcap_uri=uri, forms = c("locator_form"), 
                       raw_or_label = "haven", token=token,
                       allow_mixed_structure = TRUE)

N4_other_stbl <- read_redcap(redcap_uri=uri, forms = c("zoom_tracker_form",
                                                       "study_optout_form",
                                                       "lab_upload_form",
                                                       "baseline_consent_form",
                                                       "referral_form",
                                                       "fu1_referral_form_staff",
                                                       "practice_ema",
                                                       "qi_interviews"), 
                       raw_or_label = "haven", token=token,
                       allow_mixed_structure = TRUE)
```


```{r}
N4_screen_stbl |>
  make_labelled() |>
bind_tibbles(tbls = c("screener_1",
                      "screen_2_consent",
                      "screener_2",
                      "study_withdrawal_form"))

N4_bl_stbl |>
  make_labelled() |>
bind_tibbles(tbls = c("baseline_interview_editing"))

N4_fu1_stbl |>
  make_labelled() |>
bind_tibbles(tbls = c("follow_up_1_interview_editing"))

N4_fu2_stbl |>
  make_labelled() |>
bind_tibbles(tbls = c("follow_up_2_interview"))

N4_ema_stbl |>
  make_labelled() |>
bind_tibbles(tbls = c("ema_form",
                      "ema_burst_1_form",
                      "ema_burst_2_form",
                      "ema_burst_3_form",
                      "ema_burst_4_form",
                      "ema_burst_5_form",
                      "ema_burst_6_form",
                      "ema_burst_7_form",
                      "ema_burst_8_form",
                      "ema_daily_assessment",
                      "ema_end_of_day_assessment",
                      "ema_optout_form_staff"))

N4_blood_stbl |>
  make_labelled() |>
bind_tibbles(tbls = c("blood_draw_form"))

N4_drug_stbl |>
  make_labelled() |>
bind_tibbles(tbls = c("drug_test_form"))

N4_loc_stbl |>
  make_labelled() |>
bind_tibbles(tbls = c("locator_form"))

N4_other_stbl |>
  make_labelled() |>
bind_tibbles(tbls = c("zoom_tracker_form",
                      "study_optout_form",
                      "lab_upload_form",
                      "baseline_consent_form",
                      "referral_form",
                      "fu1_referral_form_staff",
                      "practice_ema",
                      "qi_interviews"))
```

```{r}
blint <- baseline_interview_editing
f1int <- follow_up_1_interview_editing
f2int <- follow_up_2_interview

rm(list = c("baseline_interview_editing",
            "follow_up_1_interview_editing",
            "follow_up_2_interview"))
```

```{r}
Cohort_DT <- subset(screener_1, select = c("pid","scr1_eligibility","form_status_complete")) |> 
  dplyr::rename(S1_Form = form_status_complete)

Cohort_DT <- merge(Cohort_DT, 
                   subset(screen_2_consent, select = c("pid","scr2_consent_date")),
                   all.x = TRUE, all.y = FALSE)

Cohort_DT <- merge(Cohort_DT, 
                   subset(study_optout_form, select = c("pid","opt_out_date")),
                   all.x = TRUE, all.y = FALSE)

Cohort_DT <- merge(Cohort_DT, 
                   subset(screener_2, select = c("pid","scr2_eligibility","form_status_complete")) |> 
                     dplyr::rename(S2_Form = form_status_complete),
                   all.x = TRUE, all.y = FALSE)

Cohort_DT <- merge(Cohort_DT, 
                   subset(baseline_consent_form, select = c("pid","enroll_consent")),
                   all.x = TRUE, all.y = FALSE)

Cohort_DT <- merge(Cohort_DT, 
                   subset(blint, select = c("pid","bl_date","form_status_complete")) |>
                     dplyr::rename(BL_Form = form_status_complete),
                   all.x = TRUE, all.y = FALSE)

Cohort_DT <- merge(Cohort_DT, 
                   subset(blood_draw_form, redcap_event == "baseline_interview",
                          select = c("pid","blood_vl_q2")),
                   all.x = TRUE, all.y = FALSE)

setDT(Cohort_DT)
```

```{r}
n4c_cohort <- Cohort_DT |> 
  cohort_start("Screen 1 Initiated<br>") |>
    cohort_define(
    scr1 = .full,
    s1_e = .full |> filter(scr1_eligibility == 1 & S1_Form == 2),
    s1_ie = .full |> filter(scr1_eligibility == 0 | S1_Form != 2),
    scr2 = s1_e |> filter(!is.na(scr2_consent_date) & is.na(opt_out_date)),
    s2_optout = s1_e |> filter(is.na(scr2_consent_date) | (!is.na(opt_out_date) & is.na(bl_date))),
    s2_e = scr2 |> filter(scr2_eligibility == 1 & S2_Form == 2),
    s2_ie = scr2 |> filter(scr2_eligibility == 0 | S2_Form != 2),
    enrl = s2_e |> filter(enroll_consent == 1),
    bl = .full |> filter(!is.na(bl_date)),
    det = bl |> filter(blood_vl_q2 == 0),
    undet = bl |> filter(blood_vl_q2 == 1)
    ) |>
  cohort_label(
    scr1 = "Screen 1 Initiated<br>",
    s1_e = "S1 Eligible<br>",
    s1_ie = "S1 Ineligible<br>",
    scr2 = "Screen 2 Initiated<br>",
    s2_optout = "S2 Opted Out<br>",
    s2_e = "S2 Eligible<br>",
    s2_ie = "S2 Ineligible<br>",
    enrl = "Enrolled<br>",
    bl = "Baseline Interview<br>",
    det = "Detectable VL<br>",
    undet = "Undetectable VL<br>"
  )
```

```{r}
study_consort <- n4c_cohort |>
  consort_box_add(
    "scr1", 0, 50, cohort_count_adorn(n4c_cohort, scr1)
  ) |>
    consort_box_add(
    "s1_e", 0, 40, cohort_count_adorn(n4c_cohort, s1_e)
  ) |>
    consort_box_add(
    "s1_ie", 5, 44, cohort_count_adorn(n4c_cohort, s1_ie)
  ) |>  
    consort_box_add(
    "s2_optout", 5, 33, cohort_count_adorn(n4c_cohort, s2_optout)
  ) |>  
    consort_box_add(
    "scr2", 0, 30, cohort_count_adorn(n4c_cohort, scr2)
  ) |>
    consort_box_add(
    "s2_ie", 5, 23, cohort_count_adorn(n4c_cohort, s2_ie)
  ) |>    
      consort_box_add(
    "s2_e", 0, 20, cohort_count_adorn(n4c_cohort, s2_e)
  ) |>    
      consort_box_add(
    "bl", 0, 0, cohort_count_adorn(n4c_cohort, bl)
  ) |>    
      consort_box_add(
    "det", -2, 10, cohort_count_adorn(n4c_cohort, det)
  ) |>    
      consort_box_add(
    "undet", 2, 10, cohort_count_adorn(n4c_cohort, undet)
  ) |>    
 consort_arrow_add(start = "scr1", end = "s1_e", end_side = "top") |>
  consort_arrow_add(start_x = 0, start_y = 44, end = "s1_ie", end_side = "left") |>
  consort_arrow_add(start_x = 0, start_y = 33, end = "s2_optout", end_side = "left") |>
 consort_arrow_add(start = "s1_e", end = "scr2", end_side = "top") |>
      consort_arrow_add(start_x = 0, start_y = 23, end = "s2_ie", end_side = "left") |>
     consort_arrow_add(start = "scr2", end = "s2_e", end_side = "top") |>
     consort_arrow_add(start = "s2_e", end = "bl", end_side = "top") |>
  consort_arrow_add(start = "s2_e", end = "det", end_side = "top") |>
  consort_arrow_add(start = "s2_e", end = "undet", end_side = "top")
```

```{r, include = TRUE, fig.width = 9, fig.height = 4, dev='svg'}
study_consort |>
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = 4, margin_v = 4)
```

```{r}
Enrolled <- subset(baseline_consent_form, form_status_complete == 2)$pid
NotEligible_PostEnrollment <- c("GAR030795M", "STA031097F", "ZAJ010195M")
```

```{r, echo=FALSE}
Not_Withdrawn <- setdiff(Enrolled, study_withdrawal_form$pid)
Not_Withdrawn <- setdiff(Enrolled, NotEligible_PostEnrollment)
```

```{r}
my.contin <- function (x, ...){
    with(stats.apply.rounding(stats.default(x), ...), c("",
        `Mean (SD)` = sprintf("%s (%s)", MEAN, SD), 
        `Median [Q1, Q3]` = sprintf("%s [%s, %s]", 
            MEDIAN, Q1, Q3),
        `Range [Min, Max]` = sprintf("[%s, %s]", MIN, MAX)))
}

my.missing <- function (x, ...){
    with(stats.apply.rounding(stats.default(is.na(x)), ...)$Yes, 
        c(Missing = sprintf("%s (%s%%)", FREQ, PCT)))
}

my.categ <- function (x, ...){
    c("", sapply(stats.apply.rounding(stats.default(na.omit(x)), 
        ...), function(y) with(y, sprintf("%s (%s%%)", 
        FREQ, PCT))))
}

my.render <- function(x, name, missing = any(is.na(x)), transpose = F, render.empty = "NA", 
    render.continuous = my.contin, render.categorical = my.categ, 
    render.missing = my.missing, ...) 
{
    if (is.character(render.continuous)) {
        render.continuous <- parse.abbrev.render.code(code = render.continuous, 
            ...)
    }
    if (is.character(render.categorical)) {
        render.categorical <- parse.abbrev.render.code(code = render.categorical, 
            ...)
    }
    if (is.character(render.missing)) {
        render.missing <- parse.abbrev.render.code(code = render.missing, 
            ...)
    }
    if (length(x) == 0) {
        return(render.empty)
    }
    if (is.logical(x)) {
        x <- factor(x, levels = c(T, F), labels = c("Yes", 
            "No"))
    }
    if (is.factor(x) || is.character(x)) {
        r <- do.call(render.categorical, c(list(x = x), list(...)))
    }
    else if (is.numeric(x)) {
        r <- do.call(render.continuous, c(list(x = x), list(...)))
    }
    else {
        stop(paste("Unrecognized variable type:", class(x)))
    }
    if (missing) {
        r <- c(r, do.call(render.missing, c(list(x = x), list(...))))
    }
    if (transpose) {
        if (!is.null(names(r))) {
            r <- paste0(sprintf("%s: %s", names(r), r), 
                collapse = "<br/>")
        }
        else {
            r <- paste0(r, collapse = "<br/>")
        }
    }
    r
}
```

```{r}
setDT(screener_1)
setDT(screener_2)
setDT(blint)
setDT(f1int)
setDT(f2int)
```

```{r}
bl_vars <- gsub("bl_", "", names(blint))
fu1_vars <- gsub("fu1_", "", names(f1int))
fu2_vars <- gsub("fu2_", "", names(f2int))

interview_vars <- data.frame(Variable = unique(c(bl_vars, fu1_vars, fu2_vars)))

setDT(interview_vars)

interview_vars[, BL := Variable %in% bl_vars]
interview_vars[, F1 := Variable %in% fu1_vars]
interview_vars[, F2 := Variable %in% fu2_vars]
```

```{r}
follow <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.(pid,bl_date)], 
            f1int[pid %in% Not_Withdrawn,.(pid,fu1_date)],
            f2int[pid %in% Not_Withdrawn,.(pid,fu2_date)])) |>
  melt(id.vars = c("pid"), measure.vars = patterns("date$"),
       variable.name = "Time", value.name = "Date")

follow[, Time := car::recode(Time, "'bl_date'='BL';'fu1_date'='9M';'fu2_date'='18M'", 
                             as.factor = TRUE, levels = c("BL","9M","18M"))]

follow <- na.omit(follow)
```

# Follow-Up

## Interview

```{r}
FUrate <- dcast(follow, pid ~ Time, value.var = "Date")

setnames(FUrate, old = c("BL","9M","18M"),
                 new = c("bl_date","f1_date","f2_date"))
FUrate[, Days_Since_BL := as.numeric(difftime(Sys.Date(), bl_date, units = "days"))]

FUrate[, Time_Cat := cut(Days_Since_BL, c(0,273,5000))]

FUrate[, Time_Cat := car::recode(Time_Cat, "'(0,273]'='0-273 Days';
                                        '(273,5e+03]'='274+ Days'", 
                             as.factor = TRUE,
                             levels = c('0-273 Days','274+ Days'))]

FUrate <- merge(FUrate, f1int[pid %in% Not_Withdrawn,.(pid,f1complete = form_status_complete)], all=TRUE)
FUrate <- merge(FUrate, f2int[pid %in% Not_Withdrawn,.(pid,f2complete = form_status_complete)], all=TRUE)

FUrate[, FU1_Completion := ifelse(!is.na(f1complete) & 
                                    f1complete == 2, "Yes",
                                  ifelse(Days_Since_BL > 334, "No", NA))]

FUrate[, FU2_Completion := ifelse(!is.na(f2complete) & 
                                    f2complete == 2, "Yes",
                                  ifelse(Days_Since_BL > 608, "No", NA))]

label(FUrate$FU1_Completion) <- "Nine-Month Interview Completed"
label(FUrate$FU2_Completion) <- "Eighteen-Month Interview Completed"
```

### Nine Months

```{r}
table1(~ FU1_Completion, data = FUrate[!is.na(FU1_Completion)])
```

<br>

-   n=`r nrow(FUrate[is.na(FU1_Completion) | FU1_Completion != "Yes" & Days_Since_BL <= 334])` pending nine-month follow-up interviews
-   n=`r nrow(FUrate[(is.na(FU1_Completion) | FU1_Completion != "Yes") & Days_Since_BL > 334])` missed nine-month follow-up interviews

### Eighteen Months

```{r}
table1(~ FU2_Completion, data = FUrate[!is.na(FU2_Completion)])
```

<br>

-   n=`r nrow(FUrate[is.na(FU2_Completion) | FU2_Completion != "Yes" & Days_Since_BL <= 608])` pending eighteen-month follow-up interviews
-   n=`r nrow(FUrate[(is.na(FU2_Completion) | FU2_Completion != "Yes") & Days_Since_BL > 608])` missed eighteen-month follow-up interviews

<br>

```{r}
gtsummary::tbl_cross(FUrate, row = FU1_Completion, col = FU2_Completion, 
                     percent = "cell", margin = NULL) |>
gtsummary::as_flex_table()
```

## Viral Load

```{r}
VL_follow <- subset(as_factor(blood_draw_form), !is.na(blood_vl_q2) & pid %in% Not_Withdrawn)

setDT(VL_follow)

VL_follow[, Time := car::recode(redcap_event, "'baseline_interview'='BL';
                                               'follow_up_1_interv'='9M';
                                               'follow_up_2_interv'='18M'", 
                                as.factor = TRUE, levels = c("BL","9M","18M"))]

table1(~ blood_vl_q2 | Time, 
       data = VL_follow, 
       overall = FALSE) |>
  t1flex()
```

# Withdrawals
```{r}
table1(~ as_factor(withdrawal_form), data = study_withdrawal_form) |>
  t1flex()

```

<br>

-   **n=`r nrow(study_withdrawal_form)`** withdrawals from study\
-   **n=`r sum(!(Enrolled %in% study_withdrawal_form$pid))`** enrolled participants remaining after withdrawals\

# Screen 1

```{r}
label(screener_1$scr1_contact_form) <- "Filled out online contact form?"
label(screener_1$scr1_recruit_social) <- "If called from social media advertisement, which social media platform?"
label(screener_1$scr1_consent) <- "Do you voluntarily agree to participate in this brief research interview?"
label(screener_1$scr1_residence) <- "Do you live in the New York City or Newark metropolitan area?"
label(screener_1$scr1_lang) <- "Are you able to conduct research study activities in English or Spanish?"
label(screener_1$scr1_pronouns) <- "What are your personal gender pronouns?"
label(screener_1$scr1_covid) <- "If you are found eligible for the N4 Connect Study, are you willing to follow NYU's COVID guidelines?"
label(screener_1$scr1_hivstat) <- "Have you been diagnosed as living with HIV?"
```

```{r}
table1(~ scr1_contact_form + scr1_recruit + scr1_recruit_social + scr1_consent +
         scr1_age + scr1_residence + scr1_lang + scr1_pronouns + scr1_sexbirth + 
         scr1_covid + scr1_hivstat +
         form_status_complete + scr1_eligibility, 
       data = as_factor(screener_1)) |>
  t1flex()

```

## Gender Identity

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for gender identity"

gendID_m <- melt(screener_1[, .SD, 
                    .SDcols = names(screener_1) %like% "^scr1_gidentity___\\d+|pid"], 
                id.vars = "pid")

gendID_m <- gendID_m[!value == FALSE,]
gendID_m[, Ncheck := .N, by = .(pid)]

gendID_m[Ncheck == 1, Gender_Identity := car::recode(variable, "'scr1_gidentity___1'='Man, male'; 
                                                                'scr1_gidentity___2'='Woman, female';
                                                                'scr1_gidentity___3'='Gender Non-binary';
                                                                'scr1_gidentity___4'='Transgender';
                                                                'scr1_gidentity___5'='Transman/ Transgender Man'; 
                                                                'scr1_gidentity___6'='Transfemale/ Transgender Woman'; 
                                                                'scr1_gidentity___7'='Genderqueer';
                                                                'scr1_gidentity___8'='Genderfluid';
                                                                'scr1_gidentity___9'='Questioning, or unsure of your gender identity';
                                                                'scr1_gidentity___996'='None of these describe me, other';
                                                                'scr1_gidentity___998'='Prefer not to answer'")]

gendID_m[Ncheck > 1, Gender_Identity := car::recode(variable, "else='More Than One Identity'")]

gendID_m <- unique(gendID_m[,.(pid, Gender_Identity)])
```

```{r}
label(gendID_m$Gender_Identity) <- "Gender Identity"

table1(~ Gender_Identity, data = gendID_m) |>
  t1flex()
```

-   **n=`r sum(rowSums(screener_1[, .SD, .SDcols = names(screener_1) %like% "^scr1_gidentity___\\d+"]) == 0)`** participants did not check anything\

## Sexual Orientation

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for sexual orientation"

sexor_m <- melt(screener_1[, .SD, 
                    .SDcols = names(screener_1) %like% "^scr1_sidentity1___\\d+|^scr1_sidentity2___\\d+|pid"], 
                id.vars = "pid")

sexor_m <- sexor_m[!value == FALSE,]
sexor_m[, Ncheck := .N, by = .(pid)]

sexor_m[Ncheck == 1, Sexual_Orientation := car::recode(variable, "'scr1_sidentity1___1'='Gay';
                                           'scr1_sidentity1___2'='Lesbian';
                                           'scr1_sidentity1___3'='Straight or heterosexual';
                                           'scr1_sidentity1___4'='Bisexual';
                                           'scr1_sidentity1___5'='Pansexual';
                                           'scr1_sidentity1___998'='Prefer not to answer';
                                           'scr1_sidentity2___1'='Queer';
                                           'scr1_sidentity2___2'='Polysexual, omnisexual, sapiosexual';
                                           'scr1_sidentity2___3'='Asexual';
                                           'scr1_sidentity2___4'='Two-spirit';
                                           'scr1_sidentity2___5'='Have not figured out or are in the process of figuring out your sexuality';
                                           'scr1_sidentity2___6'='Do not think of yourself as having sexuality';
                                           'scr1_sidentity2___7'='Do not use labels to identify yourself';
                                           'scr1_sidentity2___996'='Other';
                                           'scr1_sidentity2___997'='Do Not Know'")]

sexor_m[Ncheck > 1, Sexual_Orientation := car::recode(variable, "else='More Than One Orientation'")]

sexor_m <- unique(sexor_m[,.(pid, Sexual_Orientation)])
```

```{r}
label(sexor_m$Sexual_Orientation) <- "Sexual Orientation"

table1(~ Sexual_Orientation, data = sexor_m) |>
  t1flex()

```

-   **n=`r sum(rowSums(screener_1[, .SD, .SDcols = names(screener_1) %like% "^scr1_sidentity1___\\d+|^scr1_sidentity2___\\d+"]) == 0)`** participants did not check anything\

## Race/Ethnicity

```{r}
table1(~ ., data = screener_1[, .SD, .SDcols = names(screener_1) %like% "^scr1_ethnicity|^scr1_race___"]) |>
  t1flex()

```

### PHS Categories

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for PHS categories"

screener_1[, Hispanic := car::recode(as_factor(scr1_ethnicity), 
                                     "'No'='Not Hispanic or Latino';'Yes'='Hispanic or Latino';else='Unknown/Not Reported Ethnicity'", as.factor = TRUE)]
screener_1[, Hispanic := ordered(Hispanic, levels = c('Not Hispanic or Latino','Hispanic or Latino','Unknown/Not Reported Ethnicity'))]

screener_1[, Racecheck := rowSums(.SD == TRUE), .SDcols = names(screener_1) %like% "^scr1_race___[1-5]"]
screener_1[, Raceunknown := rowSums(.SD == FALSE), .SDcols = names(screener_1) %like% "^scr1_race___[1-6]"]
screener_1[, Multirace := Racecheck > 1 | scr1_race___6 == TRUE]

screener_1[, PHS_cat := case_when(
                    scr1_race___2 == TRUE & !Multirace ~ 'American Indian/Alaska Native',
                    scr1_race___3 == TRUE & !Multirace ~ 'Asian',
                    scr1_race___1 == TRUE & !Multirace ~ 'Black or African American',
                    scr1_race___5 == TRUE & !Multirace ~ 'Native Hawaiian or Other Pacific Islander',
                    scr1_race___4 == TRUE & !Multirace ~ 'White',
                    Multirace ~ 'More than One Race',
                    Raceunknown == 6 ~ 'Unknown or Not Reported')]

screener_1[, PHS_cat := ordered(PHS_cat, levels = c('American Indian/Alaska Native',
                                             'Asian',
                                             'Native Hawaiian or Other Pacific Islander',
                                             'Black or African American',
                                             'White',
                                             'More than One Race',
                                             'Unknown or Not Reported'))]

label(screener_1$PHS_cat) <- "PHS Race Category"
label(screener_1$Hispanic) <- "Ethnic Categories"

setDT(blint)
setDT(f1int)
setDT(f2int)

demog <- merge(screener_1[, .(pid, scr1_sexbirth, Hispanic, PHS_cat)],
               blint[!is.na(bl_date),.(pid,bl_date)], 
               all = TRUE)

demog[, Enrolled := pid %in% Enrolled]
demog[, Not_Withdrawn := pid %in% Not_Withdrawn]
```

```{r}
gtsummary::tbl_cross(demog, row = PHS_cat, col = Hispanic) |>
gtsummary::as_flex_table()
```

<br>

```{r}
with(as_factor(demog), 
     table(PHS_cat, Ethnicity = Hispanic, `Assigned Sex at Birth` = scr1_sexbirth)) |> 
  as.data.frame() |>
  subset(Freq > 0) |>
  dplyr::rename(`PHS Category` = PHS_cat,`Assigned Sex at Birth` = Assigned.Sex.at.Birth, Frequency = Freq) |>
  flextable() |>
  set_table_properties(width = 1, layout = "autofit")
```

# Screen 2

```{r}
label(screener_2$scr2_eligibility) <- "Is the participant preliminarily eligible?"
label(screener_2$scr2_status) <- "Enter the documentation of HIV status provided"
label(screener_2$scr2_docs) <- "Obtained copy/ photo of provided documentation?"
label(screener_2$scr2_phone) <- "Are you willing to use your own phone or a phone provided by the project for text message interviews?"

table1(~ scr2_status + scr2_docs + scr2_phone + scr2_eligibility + form_status_complete, 
       data = as_factor(screener_2[!is.na(scr2_date),])) |>
  t1flex()

```

## Opt Out

```{r}
label(study_optout_form$opt_out_reason) <- "Participation has concluded/opted-out of participation due to:"

table1(~ opt_out_reason, data = as_factor(study_optout_form)) |>
  t1flex()

```

# Enrollment

## Total

```{r, fig.width = 6, fig.asp = 0.8, out.width = "90%"}
enroll_new <- data.frame(day = seq(as.Date("2021-12-07"), as.Date("2023-11-01"), 1))

setDT(enroll_new)

enroll_new <- merge(enroll_new, 
                    blint[!is.na(bl_date), .(Enrolled = .N), by = .(bl_date)], by.x = "day", by.y = "bl_date", all=TRUE)

enroll_new[is.na(Enrolled), Enrolled := 0]
enroll_new[, Row := 1:.N]
enroll_new[, Target := 0.4258675]
enroll_new[, `Cumulative Enrolled` := cumsum(Enrolled)]
enroll_new[, `Cumulative Target` := cumsum(Target)]
enroll_new[`Cumulative Target` >= 274, `Cumulative Target` := 274]
enroll_new[, Deficit := `Cumulative Target` - `Cumulative Enrolled`]

enroll_new_m <- melt(enroll_new, id.vars = c("day","Row"), 
                     variable.name = "type",
                     value.name = "num")

# figtop <- ceiling(enroll_new_m[day == Sys.Date() & type %in% c('Cumulative Enrolled','Cumulative Target'), .(max(num))])$V1
# while(figtop %% 12 > 0) {figtop <- figtop + 1}

figtop <- 274

enroll_new_m[day > Sys.Date() & type == "Cumulative Enrolled", num := NA]

ggplot(enroll_new_m[type %in% c('Cumulative Enrolled','Cumulative Target'),], 
       aes(x = day, y = num, group = type, color = type)) + 
  geom_path() +
  scale_y_continuous(limits=c(0,275), breaks=seq(0,275,25)) +
  scale_x_date(date_breaks = "1 month", date_labels = "%b '%y") +
  ylab("Cumulative Number Enrolled") + xlab("") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size=6),
        axis.text.y = element_text(size=6),
        axis.title.y = element_text(size=6),
        legend.position="bottom", 
        legend.text=element_text(size=6),
        legend.title = element_blank())
```

```{r}
enroll_new[day == as.Date("2023-11-01"), .(`Cumulative Enrolled`, 
                                `Cumulative Target` = ceiling(`Cumulative Target`), 
                                `Current Deficit` = ceiling(Deficit))] |>
  kbl(booktabs = T, escape = F, align = "c") |>
  kable_paper("hover", full_width = FALSE)
```

# Baseline and Follow-Up Interviews

-   Three enrolled participants disclosed information which made them no longer eligible. These three participants are excluded from summaries of interview data. 

## Demographics (Baseline Sample)

### Age, Sex at Birth, and Race/Ethnicity

```{r}
table1(~ ., data = as_factor(screener_1[pid %in% Not_Withdrawn, .SD, .SDcols = names(screener_1) %like% "scr1_sexbirth$|^scr1_ethnicity|^scr1_race___|scr1_age"])) |>
  t1flex()

```

### PHS Categories

```{r,}
gtsummary::tbl_cross(demog[Enrolled == TRUE & !is.na(bl_date) & !(pid %in% NotEligible_PostEnrollment)], 
                               row = PHS_cat, col = Hispanic) |>
  gtsummary::as_flex_table()
```

<br>

```{r}
with(as_factor(demog[Enrolled == TRUE & !is.na(bl_date) & !(pid %in% NotEligible_PostEnrollment)]), 
     table(PHS_cat, Hispanic, scr1_sexbirth)) |> 
  as.data.frame() |>
  subset(Freq > 0) |>
  dplyr::rename(`PHS Category` = PHS_cat,`Assigned Sex at Birth` = scr1_sexbirth, Frequency = Freq) |>
  flextable() |>
    set_table_properties(width = 1, layout = "autofit")
```

### Gender Identity

```{r}
table1(~ Gender_Identity, data = gendID_m[pid %in% Not_Withdrawn]) |>
  t1flex()
```

### Sexual Identity

```{r}
table1(~ Sexual_Orientation, data = sexor_m[pid %in% Not_Withdrawn]) |>
  t1flex()

```

### Sexual or Gender Minority

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for sexual or gender minority"

sexmin <- merge(gendID_m, sexor_m, all = TRUE)
sexmin <- merge(sexmin, as_factor(screener_1[,.(pid, scr1_sexbirth)]), all=TRUE)

sexmin[, SO_Minority := ifelse(Sexual_Orientation == "Straight or heterosexual", "No", "Yes")]
sexmin[, GI_Minority := ifelse((Gender_Identity == "Man, male" & scr1_sexbirth == "Male") | 
                               (Gender_Identity == "Woman, female" & scr1_sexbirth == "Female"), "No", "Yes")]
```

```{r}
gtsummary::tbl_cross(sexmin[ pid %in% Not_Withdrawn,], row = SO_Minority, 
                               col = GI_Minority, percent = "cell",
                               label = list(SO_Minority ~ "Sexual Orientation Minority", GI_Minority ~ "Gender Minority")) |>
gtsummary::as_flex_table()
```

### Other Demographics

```{r}
label(blint$bl_insurance) <- "Do you currently have health insurance or health care coverage?"

table1(~ bl_immig1 + bl_immig2, 
       data = as_factor(blint[pid %in% Not_Withdrawn])) |>
  t1flex()

```

<br>

```{r}
Dem_long <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.(pid,bl_income2,bl_live1,bl_live2___1,bl_live2___2,bl_live2___3,bl_live2___4,bl_live2___5,
                                           bl_live2___6,bl_live2___7,bl_live2___996,bl_live2___998,bl_live3,bl_cjhistory1,bl_cjhistory2,
                                           bl_insurance,bl_covid1,bl_covid4,bl_awareness5,bl_awareness6,bl_rstatus___1,
                                           bl_rstatus___2,bl_rstatus___3,bl_rstatus___4,bl_rstatus___5,bl_rstatus___6,
                                           bl_rstatus___7,bl_rstatus___8,bl_rstatus___9,bl_rstatus___996,bl_rstatus___997,
                                           bl_rstatus___998,bl_sex1,bl_sex2,bl_sex3___1,bl_sex3___2,bl_sex3___3,
                                           bl_sex3___4,bl_sex3___996,bl_sex3___998,bl_education1,bl_education2,
                                           bl_employ1,bl_employ2,bl_employ4,bl_employ5,bl_income3___1,bl_income3___2,
                                           bl_income3___3,bl_income3___4,bl_income3___996,bl_income3___998,bl_street1___1,
                                           bl_street1___2,bl_street1___3,bl_street1___4,bl_street1___5,bl_street1___6,
                                           bl_street1___7,bl_street1___996,bl_street1___998,bl_street1___999)],
            f1int[pid %in% Not_Withdrawn,.(pid,fu1_income2,fu1_live1,fu1_live2___1,fu1_live2___2,fu1_live2___3,fu1_live2___4,fu1_live2___5,
                                           fu1_live2___6,fu1_live2___7,fu1_live2___996,fu1_live2___998,fu1_live3,fu1_cjhistory1,fu1_cjhistory2,
                                           fu1_insurance,fu1_covid1,fu1_covid4,fu1_awareness5,fu1_awareness6,fu1_rstatus___1,
                                           fu1_rstatus___2,fu1_rstatus___3,fu1_rstatus___4,fu1_rstatus___5,fu1_rstatus___6,
                                           fu1_rstatus___7,fu1_rstatus___8,fu1_rstatus___9,fu1_rstatus___996,fu1_rstatus___997,
                                           fu1_rstatus___998,fu1_sex1,fu1_sex2,fu1_sex3___1,fu1_sex3___2,fu1_sex3___3,
                                           fu1_sex3___4,fu1_sex3___996,fu1_sex3___998,fu1_education1,fu1_education2,
                                           fu1_employ1,fu1_employ2,fu1_employ4,fu1_employ5,fu1_income3___1,fu1_income3___2,
                                           fu1_income3___3,fu1_income3___4,fu1_income3___996,fu1_income3___998,fu1_street1___1,
                                           fu1_street1___2,fu1_street1___3,fu1_street1___4,fu1_street1___5,fu1_street1___6,
                                           fu1_street1___7,fu1_street1___996,fu1_street1___998,fu1_street1___999)],
            f2int[pid %in% Not_Withdrawn,.(pid,fu2_income2,fu2_live1,fu2_live2___1,fu2_live2___2,fu2_live2___3,fu2_live2___4,fu2_live2___5,
                                           fu2_live2___6,fu2_live2___7,fu2_live2___996,fu2_live2___998,fu2_live3,fu2_cjhistory1,fu2_cjhistory2,
                                           fu2_insurance,fu2_covid1,fu2_covid4,fu2_awareness5,fu2_awareness6,fu2_rstatus___1,
                                           fu2_rstatus___2,fu2_rstatus___3,fu2_rstatus___4,fu2_rstatus___5,fu2_rstatus___6,
                                           fu2_rstatus___7,fu2_rstatus___8,fu2_rstatus___9,fu2_rstatus___996,fu2_rstatus___997,
                                           fu2_rstatus___998,fu2_sex1,fu2_sex2,fu2_sex3___1,fu2_sex3___2,fu2_sex3___3,
                                           fu2_sex3___4,fu2_sex3___996,fu2_sex3___998,fu2_education1,fu2_education2,
                                           fu2_employ1,fu2_employ2,fu2_employ4,fu2_employ5,fu2_income3___1,fu2_income3___2,
                                           fu2_income3___3,fu2_income3___4,fu2_income3___996,fu2_income3___998,fu2_street1___1,
                                           fu2_street1___2,fu2_street1___3,fu2_street1___4,fu2_street1___5,fu2_street1___6,
                                           fu2_street1___7,fu2_street1___996,fu2_street1___998,fu2_street1___999)]))

Dem_long_m <- melt(Dem_long, id.vars = "pid",
                   measure.vars = patterns("income2$","live1$","live2___1$","live2___2$","live2___3$","live2___4$","live2___5$",
                                           "live2___6$","live2___7$","live2___996$","live2___998$","live3$","cjhistory1$","cjhistory2$",
                                           "insurance$","covid1$","covid4$","awareness5$","awareness6$","rstatus___1$",
                                           "rstatus___2$","rstatus___3$","rstatus___4$","rstatus___5$","rstatus___6$",
                                           "rstatus___7$","rstatus___8$","rstatus___9$","rstatus___996$","rstatus___997$",
                                           "rstatus___998$","sex1$","sex2$","sex3___1$","sex3___2$","sex3___3$",
                                           "sex3___4$","sex3___996$","sex3___998$","education1$","education2$",
                                           "employ1$","employ2$","employ4$","employ5$","income3___1$","income3___2$",
                                           "income3___3$","income3___4$","income3___996$","income3___998$","street1___1$",
                                           "street1___2$","street1___3$","street1___4$","street1___5$","street1___6$",
                                           "street1___7$","street1___996$","street1___998$","street1___999$"),
                   variable.name = "Time", value.name = c("income2","live1","live2___1","live2___2","live2___3","live2___4","live2___5",
                                           "live2___6","live2___7","live2___996","live2___998","live3","cjhistory1","cjhistory2",
                                           "insurance","covid1","covid4","awareness5","awareness6","rstatus___1",
                                           "rstatus___2","rstatus___3","rstatus___4","rstatus___5","rstatus___6",
                                           "rstatus___7","rstatus___8","rstatus___9","rstatus___996","rstatus___997",
                                           "rstatus___998","sex1","sex2","sex3___1","sex3___2","sex3___3",
                                           "sex3___4","sex3___996","sex3___998","education1","education2",
                                           "employ1","employ2","employ4","employ5","income3___1","income3___2",
                                           "income3___3","income3___4","income3___996","income3___998","street1___1",
                                           "street1___2","street1___3","street1___4","street1___5","street1___6",
                                           "street1___7","street1___996","street1___998","street1___999"))

Dem_long_m[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", 
                                 as.factor = TRUE, levels = c('BL','9M','18M'))]

Dem_long_m <- merge(Dem_long_m, follow[,.(pid,Time)], all = FALSE)

Dem_long_m[, sex2 := as.numeric(sex2)]

label(Dem_long_m$sex2) <- "How old were you when you had sexual intercourse for the first time with somebody else?"
```

```{r}
table1(~ income2 + live1 + live2___1 + live2___2 + live2___3 + live2___4 + live2___5 + 
         live2___6 + live2___7 + live2___996 + live2___998 + live3 + 
         insurance + covid1 + covid4 + awareness5 + awareness6 + rstatus___1 + 
         rstatus___2 + rstatus___3 + rstatus___4 + rstatus___5 + rstatus___6 + 
         rstatus___7 + rstatus___8 + rstatus___9 + rstatus___996 + rstatus___997 + 
         rstatus___998 + sex1 + sex2 + sex3___1 + sex3___2 + sex3___3 + 
         sex3___4 + sex3___996 + sex3___998 + education1 + education2 + 
         employ1 + employ2 + employ4 + income3___1 + income3___2 + 
         income3___3 + income3___4 + income3___996 + income3___998 + street1___1 + 
         street1___2 + street1___3 + street1___4 + street1___5 + street1___6 + 
         street1___7 + street1___996 + street1___998 + street1___999 | Time, 
       data = as_factor(Dem_long_m), overall = FALSE, render = my.render) |>
  t1flex()
```

<br>

```{r}
Dem_CJI <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.(pid,bl_cjhistory1,bl_cjhistory2)],
            f1int[pid %in% Not_Withdrawn,.(pid,fu1_cjhistory1,fu1_cjhistory2)],
            f2int[pid %in% Not_Withdrawn,.(pid,fu2_cjhistory1,fu2_cjhistory2)]))

label(Dem_CJI$fu1_cjhistory1) <- "How many times in the past 9 months have you been stopped or harassed by the police? [9M Follow-Up]"
label(Dem_CJI$fu2_cjhistory1) <- "How many times in the past 9 months have you been stopped or harassed by the police? [18M Follow-Up]"
label(Dem_CJI$fu1_cjhistory2) <- "How many times in the past 9 months have you spent one or more nights in a jail, prison, or detention facility? [9M Follow-Up]"
label(Dem_CJI$fu2_cjhistory2) <- "How many times in the past 9 months have you spent one or more nights in a jail, prison, or detention facility? [18M Follow-Up]"
```

```{r}
table1(~ bl_cjhistory1 + fu1_cjhistory1 + fu2_cjhistory1 +
         bl_cjhistory2 + fu1_cjhistory2 + fu2_cjhistory2, data = as_factor(Dem_CJI),
       render = my.render) |>
  t1flex()
```

<br>

## Multigroup Ethnic Identity

[Phinney, J. S., & Ong, A. D. (2007). Conceptualization and measurement of ethnic identity: Current status and future directions.Journal of Counseling Psychology, 54(3), 271--281. https://doi.org/10.1037/0022-0167.54.3.271](https://psycnet.apa.org/fulltext/2007-09249-006.html)


```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for multigroup ethnic identity"

MEI_L <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.(pid,bl_identity1,bl_identity2,bl_identity3,bl_identity4,bl_identity5,bl_identity6)], 
            f1int[pid %in% Not_Withdrawn,.(pid,fu1_identity1,fu1_identity2,fu1_identity3,fu1_identity4,fu1_identity5,fu1_identity6)],
            f2int[pid %in% Not_Withdrawn,.(pid,fu2_identity1,fu2_identity2,fu2_identity3,fu2_identity4,fu2_identity5,fu2_identity6)]))

MEI_L <- melt(MEI_L, id.vars = "pid", 
                 measure.vars = patterns("identity1$","identity2$","identity3$",
                                         "identity4$","identity5$","identity6$"),
                 variable.name = "Time", value.name = c("identity1","identity2","identity3",
                                                        "identity4","identity5","identity6"))

MEI_L[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

MEI_m <- melt(MEI_L, id.vars = c("pid","Time"), variable.name = "Item", value.name = "Response")

MEI_m[, Response_n := ifelse(Response %in% 1:5, Response, as.integer(NA))]
```

```{r}
table1(~ identity1 + identity2 + identity3 + identity4 + identity5 + identity6 | Time, 
       data = as_factor(merge(na.omit(follow), MEI_L)), 
       render = my.render, overall = FALSE) |>
  t1flex()

```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(MEI_m[Time == "BL",.(pid, Response_n, Item)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## Sexual Orientation Identity

[Toomey, R. B., Anhalt, K., & Shramko, M. (2016). An examination of the validity and reliability of a measure of sexual orientation identity exploration, resolution, and affirmation. Self and Identity, 15(4), 488-504.](https://www.tandfonline.com/doi/full/10.1080/15298868.2016.1157516)

-   Items administered to the subset of participants not reporting a "straight" sexual orientation

```{r}
table1(~ bl_soidentity1 + bl_soidentity2 + bl_soidentity3 + bl_soidentity4 +
         bl_soidentity5 + bl_soidentity6, 
       data = as_factor(blint[pid %in% Not_Withdrawn,]), 
       render = my.render) |>
  t1flex()

```

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for sexual orientation identity"

SOI_m <- melt(blint[pid %in% Not_Withdrawn, 
   .(pid, bl_soidentity1,bl_soidentity2,bl_soidentity3,
          bl_soidentity4,bl_soidentity5,bl_soidentity6)],
   id.vars = "pid", variable.name = "Item", value.name = "Response")

SOI_m[, Response_n := ifelse(Response %in% 0:3, Response, as.integer(NA))]
```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(SOI_m[,.(pid, Response_n, Item)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## Genderqueer Identity

[McGuire, J. K., Beek, T. F., Catalpa, J. M., & Steensma, T. D. (2019). The Genderqueer Identity (GQI) Scale: Measurement and validation of four distinct subscales with trans and LGBQ clinical and community samples in two countries. International Journal of Transgenderism, 20(2-3), 289-304.](https://www.tandfonline.com/doi/full/10.1080/15532739.2018.1460735)

-   Items administered to the subset of participants reporting a sex assigned at birth which did not match their current gender identity
-   One item from each subscale administered

```{r}
table1(~ bl_gqidentity1 + bl_gqidentity2 + bl_gqidentity3 + bl_gqidentity4, 
       data = as_factor(blint[pid %in% Not_Withdrawn,]), 
       render = my.render) |>
  t1flex()

```

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for genderqueer identity"

GQI_m <- melt(blint[pid %in% Not_Withdrawn, 
   .(pid, bl_gqidentity1, bl_gqidentity2, bl_gqidentity3, bl_gqidentity4)],
   id.vars = "pid", variable.name = "Item", value.name = "Response")

GQI_m[, Response_n := ifelse(Response %in% 0:4, Response, as.integer(NA))]
```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(GQI_m[,.(pid, Response_n, Item)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## Physical and Mental Health

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for physical and mental health"

Health_L <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[,.(pid,bl_health1,bl_health2)], 
            f1int[,.(pid,fu1_health1,fu1_health2)],
            f2int[,.(pid,fu2_health1,fu2_health2)]))

Health_L <- melt(Health_L, id.vars = "pid", 
                 measure.vars = list(c("bl_health1","fu1_health1","fu2_health1"), 
                                     c("bl_health2","fu1_health2","fu2_health2")),
                 variable.name = "Time", value.name = c("health1","health2"))

Health_L[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]
```

```{r}
table1(~ health1 + health2 | Time, 
       data = na.omit(as_factor(Health_L[pid %in% Not_Withdrawn,])), 
       overall = FALSE,
       render = my.render) |>
  t1flex()

```


## Diagnosis

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for HIV diagnosis"

HIVdx <- merge(screener_1[pid %in% Not_Withdrawn, .(pid, scr1_age)],
               blint[pid %in% Not_Withdrawn,.(pid, bl_date, bl_diagnosis1, 
                                              bl_diagnosis2, bl_diagnosis3,bl_diagnosis4)])

HIVdx[, Years_HIV := scr1_age - bl_diagnosis2]
HIVdx[Years_HIV < 0, Years_HIV := 0]

label(HIVdx$Years_HIV) <- "Years Living with HIV at Baseline"
```

```{r}
table1(~ bl_diagnosis1 + bl_diagnosis2 + Years_HIV + bl_diagnosis3 + bl_diagnosis4, 
       data = as_factor(HIVdx)) |>
  t1flex()

```

## ART

### Recent

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for recent ART"

ARTVAS_L <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.(pid,bl_artvas1,bl_artvas2,bl_artvas2a,bl_artvas3)], 
            f1int[pid %in% Not_Withdrawn,.(pid,fu1_artvas1,fu1_artvas2,fu1_artvas2a,fu1_artvas3)],
            f2int[pid %in% Not_Withdrawn,.(pid,fu2_artvas1,fu2_artvas2,fu2_artvas2a,fu2_artvas3)]))

ARTVAS_L <- melt(ARTVAS_L, id.vars = "pid", 
                 measure.vars = patterns("vas1$","vas2$","vas2a$","vas3$"),
                 variable.name = "Time", value.name = c("artvas1","artvas2","artvas2a","artvas3"))

ARTVAS_L[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

ARTVAS_L <- merge(ARTVAS_L, follow[,.(pid,Time)])
```

```{r}
table1(~ artvas2 + artvas2a + artvas3 | Time, 
       data = merge(na.omit(follow), as_factor(ARTVAS_L[pid %in% Not_Withdrawn,])), 
       overall = FALSE,
       render = my.render) |>
  t1flex()
```

### History/Current Regimen

```{r}
blint[bl_art3 == -997, bl_art3 := NA]

table1(~ bl_art1 + bl_art_inj1 + bl_art2 + bl_art3 + bl_art4 + bl_art5, 
       data = as_factor(blint[pid %in% Not_Withdrawn,])) |>
  t1flex()

```

## HIV Care

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for HIV Care"

HIV_Care <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[,.SD, .SDcols = names(blint) %like% "hivcare\\d+$|hivcare$|pid"], 
            f1int[,.SD, .SDcols = names(f1int) %like% "hivcare\\d+$|hivcare$|pid"],
            f2int[,.SD, .SDcols = names(f2int) %like% "hivcare\\d+$|hivcare$|pid"]))

HIV_Care <- melt(HIV_Care, id.var = "pid",
                 measure.vars = patterns("care$","care1$","care2$","care3$","care4$",
                                         "care6$","care7$"),
                 variable.name = "Time",
                 value.name = c("hivcare","hivcare1","hivcare2","hivcare3","hivcare4",
                                "hivcare6","hivcare7"))

HIV_Care[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

HIV_Care <- merge(HIV_Care, follow[,.(pid,Time)])
```

```{r}
table1(~ hivcare + hivcare1 + hivcare3 + hivcare4 + hivcare6 + hivcare7 | Time, 
       data = as_factor(HIV_Care), overall = FALSE) |>
  t1flex()

```

## Reasons for sometimes stopping or discontinuing ART

```{r}
table1(~ ., data = as_factor(blint[pid %in% Not_Withdrawn & bl_art1 == 1 & bl_art4 > 0, 
                      .SD, .SDcols = names(blint) %like% "bl_stopart\\d+$"])) |>
  t1flex()

```

## Reasons for never taking ART

```{r}
table1(~ ., data = as_factor(blint[pid %in% Not_Withdrawn & bl_art1 == 0, 
                      .SD, .SDcols = names(blint) %like% "bl_neverart\\d+$"])) |>
  t1flex()

```

## Motivation

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for motivation"

Motivation_L <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[,.SD, .SDcols = names(blint) %like% "motivation\\d+$|pid"], 
            f1int[,.SD, .SDcols = names(f1int) %like% "motivation\\d+$|pid"],
            f2int[,.SD, .SDcols = names(f2int) %like% "motivation\\d+$|pid"]))

Motivation_L <- melt(Motivation_L, id.vars = "pid", 
                 measure.vars = patterns("n1$", "n2$", "n3$", "n4$", "n5$", 
                                         "n6$", "n7$", "n8$", "n9$", "n10$",
                                         "n11$", "n12$"),
                 variable.name = "Time",
                 value.name = paste("motivation", 1:12, sep=""))

Motivation_L[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

Motivation_L <- merge(follow[,.(pid,Time)], Motivation_L)

table1(~ motivation1 + motivation2 + motivation3 + motivation4 + motivation5 + motivation6 + 
         motivation7 + motivation8 + motivation9 + motivation10 + motivation11 + motivation12 | Time, 
       data = merge(na.omit(follow), as_factor(Motivation_L[pid %in% Not_Withdrawn,])), 
       overall = FALSE,
       render = my.render) |>
  t1flex()

```

## Life Outcome Expectancies

[Hussen, S. A., Harper, G. W., Bauermeister, J. A., Hightow-Weidman, L. B., & Adolescent Medicine Trials Network for HIV/AIDS Interventions. (2015). Psychosocial influences on engagement in care among HIV-positive young black gay/bisexual and other men who have sex with men. AIDS patient care and STDs, 29(2), 77-85.](https://www.liebertpub.com/doi/full/10.1089/apc.2014.0117)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for life outcome expectancies"

LifeOutcome_L <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_outcome\\d+$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_outcome\\d+$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_outcome\\d+$|pid"]))

LifeOutcome_L <- melt(LifeOutcome_L, id.vars = "pid",
                      measure.vars = patterns("me1$","me2$","me3$","me4$","me5$","me6$",
                                              "me7$","me8$","me9$","me10$","me11$","me12$"),
                      variable.name = "Time",
                      value.name = paste("outcome", 1:12, sep=""))

LifeOutcome_L[is.na(outcome11) & outcome10 == 4, outcome11 := 4]
LifeOutcome_L[is.na(outcome12) & outcome11 == 4, outcome12 := 4]

LifeOutcome_L[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

LifeOutcome_L <- merge(LifeOutcome_L, follow[,.(pid,Time)])
```

```{r}
table1(~ .| Time, data = as_factor(LifeOutcome_L[, .SD, .SDcols = names(LifeOutcome_L) %like% "outcome\\d|Time"]), 
       overall = FALSE) |>
  t1flex()

```

## IPV

[Goldenberg, T., Jadwin-Cakmak, L., & Harper, G. W. (2018). Intimate partner violence among transgender youth: Associations with intrapersonal and structural factors. Violence and gender, 5(1), 19-25.](https://www.liebertpub.com/doi/full/10.1089/vio.2017.0041)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for IPV"

IPV_L <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_ipv\\d+$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_ipv\\d+$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_ipv\\d+$|pid"]))

IPV_L <- melt(IPV_L, id.vars = "pid",
              measure.vars = patterns("ipv1$","ipv2$","ipv3$","ipv4$"),
              variable.name = "Time",
              value.name = c("ipv1","ipv2","ipv3","ipv4"))

IPV_L[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

IPV_L[is.na(ipv3) & ipv1 == 0, ipv3 := 0]
IPV_L[is.na(ipv4) & ipv2 == 0, ipv4 := 0]

IPV_L <- merge(IPV_L, na.omit(follow))

table1(~ .| Time, data = as_factor(IPV_L[, .SD, .SDcols = names(IPV_L) %like% "ipv\\d|Time"]), 
       overall = FALSE) |>
  t1flex()

```

## Social Support

[Sherbourne, C. D., & Stewart, A. L. (1991). The MOS social support survey. Social science & medicine, 32(6), 705-714.](https://www.sciencedirect.com/science/article/abs/pii/027795369190150B)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for social support"

socsup <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_mos\\d+$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_mos\\d+$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_mos\\d+$|pid"]))

socsup <- melt(socsup, id.vars = "pid",
               measure.vars = patterns("mos1$","mos2$","mos3$","mos4$","mos5$","mos6$","mos7$","mos8$","mos9$"),
               variable.name = "Time",
               value.name = paste("mos", 1:9, sep = ""))

socsup[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

socsup <- merge(na.omit(follow), socsup)

socsup_m <- melt(socsup, id.vars = c("pid","Time","Date"),
                 variable.name = "Item", value.name = "Response")

socsup_m[, Response_n := ifelse(Response %in% 1:5, Response - 1, as.integer(NA))]

socsup <- merge(socsup,
      socsup_m[, .(Social_Support = mean(Response_n, na.rm = TRUE)*9 / 36 * 100), by = .(pid,Time)],
      by = c("pid","Time"))

label(socsup$Social_Support) <- "Social Support Total Score"
```

```{r}
table1(~ . | Time, data = as_factor(socsup[, .SD, .SDcols = names(socsup) %like% "mos\\d|Support|Time"]),
       overall = FALSE) |>
  t1flex()

```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(socsup_m[Time == "BL",.(pid,Item,Response_n)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## Everyday Discrimination

[Williams, D. R., Yu, Y., Jackson, J. S., & Anderson, N. B. (1997). Racial differences in physical and mental health: Socio-economic status, stress and discrimination. Journal of health psychology, 2(3), 335-351.](https://journals.sagepub.com/doi/abs/10.1177/135910539700200305)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for everyday discrimination"

edd <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_discrim\\d+$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_discrim\\d+$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_discrim\\d+$|pid"]))

edd <- melt(edd, id.vars = "pid",
               measure.vars = patterns("discrim1$","discrim2$","discrim3$","discrim4$","discrim5$",
                                       "discrim6$","discrim7$","discrim8$","discrim9$"),
               variable.name = "Time",
               value.name = paste("discrim", 1:9, sep = ""))

edd[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

edd <- merge(na.omit(follow), edd)

edd_m <- melt(edd, id.vars = c("pid","Time","Date"),
                 variable.name = "Item", value.name = "Response")

edd_m[, Response_n := ifelse(Response %in% 1:6, Response, as.integer(NA))]

edd <- merge(edd,
      edd_m[, .(Everyday_Discrimination = mean(Response_n, na.rm = TRUE)*9), by = .(pid,Time)],
      by = c("pid","Time"))

label(edd$Everyday_Discrimination) <- "Everyday Discrimination Total Score"
```

```{r}
table1(~ . | Time, data = as_factor(edd[, .SD, .SDcols = names(edd) %like% "discrim\\d+$|Discrim|Time"]),
       overall = FALSE) |>
  t1flex()

```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(edd_m[Time == "BL",.(pid,Item,Response_n)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## HIV Stigma

[Wright, K., Naar-King, S., Lam, P., Templin, T., & Frey, M. (2007). Stigma scale revised: reliability and validity of a brief measure of stigma for HIV+ youth. Journal of adolescent health, 40(1), 96-98.](https://www.sciencedirect.com/science/article/pii/S1054139X06003004)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for HIV stigma"

stig <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_stigma\\d+$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_stigma\\d+$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_stigma\\d+$|pid"]))

stig <- melt(stig, id.vars = "pid",
               measure.vars = patterns("stigma1$","stigma2$","stigma3$","stigma4$","stigma5$",
                                       "stigma6$","stigma7$","stigma8$","stigma9$","stigma10$"),
               variable.name = "Time",
               value.name = paste("stigma", 1:10, sep = ""))

stig[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

stig <- merge(na.omit(follow), stig)

stig_m <- melt(stig, id.vars = c("pid","Time","Date"),
                 variable.name = "Item", value.name = "Response")

stig_m[, Response_n := ifelse(Response %in% 1:4, Response, as.integer(NA))]

stig <- merge(stig,
      stig_m[, .(HIV_Stigma = mean(Response_n, na.rm = TRUE)*10), by = .(pid,Time)],
      by = c("pid","Time"))

label(stig$HIV_Stigma) <- "HIV Stigma Total Score"
```

```{r}
table1(~ . | Time, data = as_factor(stig[, .SD, .SDcols = names(stig) %like% "stigma\\d+$|Stigma|Time"]),
       overall = FALSE) |>
  t1flex()

```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(stig_m[Time == "BL",.(pid,Item,Response_n)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## Client Engagement in HIV Care

[Yatchmenoff, D. K. (2005). Measuring client engagement from the client's perspective in nonvoluntary child protective services. Research on social work practice, 15(2), 84-96.](https://journals.sagepub.com/doi/abs/10.1177/1049731504271605)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for client engagement in HIV care"

engage <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_clientcare\\d+$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_clientcare\\d+$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_clientcare\\d+$|pid"]))

engage <- melt(engage, id.vars = "pid",
               measure.vars = patterns("clientcare1$","clientcare2$","clientcare3$","clientcare4$",
                                       "clientcare5$","clientcare6$","clientcare7$","clientcare8$"),
               variable.name = "Time",
               value.name = paste("clientcare", 1:8, sep = ""))

engage[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

engage <- merge(na.omit(follow), engage)

engage_m <- melt(engage, id.vars = c("pid","Time","Date"),
                 variable.name = "Item", value.name = "Response")
engage_m[, Item := as.numeric(gsub("clientcare","",Item))]
engage_m[Item %in% c(1,3,4,5,6,8), Response_n := ifelse(Response %in% 1:5, Response - 1, as.integer(NA))]
engage_m[Item %in% c(2,7), Response_n := ifelse(Response %in% 1:5, 4 - (Response - 1), as.integer(NA))]

engage <- merge(engage,
      engage_m[, .(Care_Engage = mean(Response_n, na.rm = TRUE)*8), by = .(pid,Time)],
      by = c("pid","Time"))

label(engage$Care_Engage) <- "HIV Care Engagement Total Score"
```

```{r}
table1(~ . | Time, data = as_factor(engage[, .SD, .SDcols = names(engage) %like% "clientcare\\d|Engage|Time"]),
       overall = FALSE) |>
  t1flex()

```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(engage_m[Time == "BL",.(pid,Item,Response_n)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## HIV Care Satisfaction

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for HIV care satisfaction"

caresat <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_spns\\d+$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_spns\\d+$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_spns\\d+$|pid"]))

caresat <- melt(caresat, id.vars = "pid",
               measure.vars = patterns("spns1$","spns2$"),
               variable.name = "Time",
               value.name = paste("spns", 1:2, sep = ""))

caresat[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

caresat <- merge(na.omit(follow), caresat)

caresat_m <- melt(caresat, id.vars = c("pid","Time","Date"),
                 variable.name = "Item", value.name = "Response")

caresat_m[, Response_n := ifelse(Response %in% 1:5, Response - 1, as.integer(NA))]

caresat <- merge(caresat,
      caresat_m[, .(Care_Satisfaction = mean(Response_n, na.rm = TRUE)*2), by = .(pid,Time)],
      by = c("pid","Time"))

label(caresat$Care_Satisfaction) <- "HIV Care Satisfaction Total Score"
```

```{r}
table1(~ . | Time, data = as_factor(caresat[, .SD, .SDcols = names(caresat) %like% "spns\\d|Satis|Time"]),
       overall = FALSE) |>
  t1flex()

```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(caresat_m[Time == "BL",.(pid,Item,Response_n)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## Trust in Provider

[Anderson, L. A., & Dedrick, R. F. (1990). Development of the Trust in Physician scale: a measure to assess interpersonal trust in patient-physician relationships. Psychological reports, 67(3_suppl), 1091-1100.](https://journals.sagepub.com/doi/abs/10.2466/pr0.1990.67.3f.1091)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for trust in provider"

trust <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_trust\\d+$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_trust\\d+$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_trust\\d+$|pid"]))

trust <- melt(trust, id.vars = "pid",
               measure.vars = patterns("trust1$","trust2$","trust3$","trust4$",
                                       "trust5$","trust6$","trust7$","trust8$",
                                       "trust9$","trust10$","trust11$"),
               variable.name = "Time",
               value.name = paste("trust", 1:11, sep = ""))

trust[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

trust <- merge(na.omit(follow), trust)

trust_m <- melt(trust, id.vars = c("pid","Time","Date"),
                 variable.name = "Item", value.name = "Response")
trust_m[, Item := as.numeric(gsub("trust","",Item))]
trust_m[Item %in% c(2,3,4,6,7,9,10), Response_n := ifelse(Response %in% 1:5, Response - 1, as.integer(NA))]
trust_m[Item %in% c(1,5,7,11), Response_n := ifelse(Response %in% 1:5, 4 - (Response - 1), as.integer(NA))]

trust <- merge(trust,
      trust_m[, .(Provider_Trust = mean(Response_n, na.rm = TRUE)*11), by = .(pid,Time)],
      by = c("pid","Time"))

label(trust$Provider_Trust) <- "Provider Trust Total Score"
```

```{r}
table1(~ . | Time, data = as_factor(trust[, .SD, .SDcols = names(trust) %like% "trust\\d|Trust|Time"]),
       overall = FALSE) |>
  t1flex()

```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(trust_m[Time == "BL",.(pid,Item,Response_n)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## ART Outcome Expectancies

[Erlen, J. A., Cha, E. S., Kim, K. H., Caruthers, D., & Sereika, S. M. (2010). The HIV Medication Taking Selfefficacy Scale: Psychometric evaluation. Journal of advanced nursing, 66(11), 2560-2572.](https://onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2648.2010.05400.x)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for ART outcome expectancies"

erlen_oe <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_artoutcome1[a-g]$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_artoutcome1[a-g]$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_artoutcome1[a-g]_v2|pid"]))

erlen_oe <- melt(erlen_oe, id.vars = "pid",
               measure.vars = patterns("1a","1b","1c","1d",
                                       "1e","1f","1g"),
               variable.name = "Time",
               value.name = paste("artoutcome1", letters[1:7], sep = ""))

erlen_oe[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

erlen_oe <- merge(na.omit(follow), erlen_oe)

erlen_oe_m <- melt(erlen_oe, id.vars = c("pid","Time","Date"),
                 variable.name = "Item", value.name = "Response")

erlen_oe_m[, Response_n := ifelse(Response %in% 1:10, Response, as.integer(NA))]

erlen_oe <- merge(erlen_oe,
      erlen_oe_m[, .(Outcome_Expectancy = mean(Response_n, na.rm = TRUE)), by = .(pid,Time)],
      by = c("pid","Time"))

label(erlen_oe$Outcome_Expectancy) <- "ART Outcome Expectancy Total Score"
```

```{r}
table1(~ . | Time, data = as_factor(erlen_oe[, .SD, .SDcols = names(erlen_oe) %like% "come1[a-g]|Expect|Time"]),
       overall = FALSE) |>
  t1flex()

```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(erlen_oe_m[Time == "BL",.(pid,Item,Response_n)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## ART Self-Efficacy

[Erlen, J. A., Cha, E. S., Kim, K. H., Caruthers, D., & Sereika, S. M. (2010). The HIV Medication Taking Selfefficacy Scale: Psychometric evaluation. Journal of advanced nursing, 66(11), 2560-2572.](https://onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2648.2010.05400.x)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for ART self-efficacy"

erlen_mse <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_artadh\\d|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_artadh\\d|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_artadh\\d|pid"]))

erlen_mse <- melt(erlen_mse, id.vars = "pid",
               measure.vars = patterns("adh1$","adh2$","adh3$","adh4$","adh5$",
                                       "adh6$","adh7$","adh8$","adh9$","adh10$",
                                       "adh11$","adh12$","adh13$","adh14$","adh15$"),
               variable.name = "Time",
               value.name = paste("artadh", 1:15, sep = ""))

erlen_mse[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

erlen_mse <- merge(na.omit(follow), erlen_mse)

erlen_mse_m <- melt(erlen_mse, id.vars = c("pid","Time","Date"),
                 variable.name = "Item", value.name = "Response")

erlen_mse_m[, Response_n := ifelse(Response %in% 1:10, Response, as.integer(NA))]

erlen_mse <- merge(erlen_mse,
      erlen_mse_m[, .(Medication_Self_Efficacy = mean(Response_n, na.rm = TRUE)), by = .(pid,Time)],
      by = c("pid","Time"))

label(erlen_mse$Medication_Self_Efficacy) <- "ART Medication Self Efficacy Total Score"
```

```{r}
table1(~ . | Time, data = as_factor(erlen_mse[, .SD, .SDcols = names(erlen_mse) %like% "adh\\d$|Efficacy|Time"]),
       overall = FALSE) |>
  t1flex()

```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(erlen_mse_m[Time == "BL",.(pid,Item,Response_n)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## ACES

[Finkelhor, D., Shattuck, A., Turner, H., & Hamby, S. (2015). A revised inventory of adverse childhood experiences. Child abuse & neglect, 48, 13-21.](https://www.sciencedirect.com/science/article/pii/S0145213415002409)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for ACES"

ACES <- blint[pid %in% Not_Withdrawn, .SD, .SDcols = names(blint) %like% "pid|bl_aces\\d"]

ACES[, Eabuse := ifelse(bl_aces1 == 1 | bl_aces2 == 1, "Yes", "No")]
ACES[, Pabuse := ifelse(bl_aces3 == 1 | bl_aces4 == 1, "Yes", "No")]
ACES[, Sassault := ifelse(bl_aces5 == 1 | bl_aces6 == 1, "Yes", "No")]
ACES[, Eneglect := ifelse(bl_aces7 == 1 | bl_aces8 == 1, "Yes", "No")]
ACES[, Pneglect := ifelse(bl_aces9 == 1 | bl_aces10 == 1, "Yes", "No")]
ACES[, Pardivsep := ifelse(bl_aces11 == 1, "Yes", "No")]
ACES[, Mothviol := ifelse(bl_aces12 == 1 | bl_aces13 == 1 | bl_aces14 == 1, "Yes", "No")] 
ACES[, FamSU := ifelse(bl_aces15 == 1, "Yes", "No")] 
ACES[, FamMH := ifelse(bl_aces16 == 1, "Yes", "No")]
ACES[, Parprison := ifelse(bl_aces17 == 1, "Yes", "No")]
ACES[, LowSES := ifelse(bl_aces21 == 1, "Yes", "No")]
ACES[, peervic := ifelse(bl_aces18 == 1, "Yes", "No")]
ACES[, peerisol := ifelse(bl_aces19 == 1, "Yes", "No")]
ACES[, Commviol := ifelse(bl_aces20 == 1, "Yes", "No")]

ACES_cols <- c("pid","Eabuse","Pabuse","Sassault","Eneglect",
               "Pneglect","Pardivsep","Mothviol","FamSU","FamMH",
               "Parprison","LowSES","peervic","peerisol","Commviol")

ACES_m <- melt(ACES[, .SD, .SDcols = ACES_cols], id.vars = "pid")

ACES <- merge(ACES, ACES_m[, .(ACES_sum = sum(value == "Yes")), by = .(pid)])

label(ACES$ACES_sum) <- "ACES Sum (0-14)"
```

```{r}
table1(~ ., data = as_factor(ACES[, .SD, .SDcols = names(ACES) %like% "bl_aces\\d|ACES_sum"])) |>
  t1flex()

```

## Social Network Members

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for social network members"

snet <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "person[1-5][a-n]|person[1-5]|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "person[1-5][a-n]|person[1-5]|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "person[1-5][a-n]|person[1-5]|pid"]))

sn <- melt(snet, id.vars = c("pid"),
              measure.vars = patterns("son1$","son2$","son3$","son4$","son5$",
                         "son1a$","son2a$","son3a$","son4a$","son5a$",
                         "son1b$","son2b$","son3b$","son4b$","son5b$",
                         "son1c___1$","son2c___1$","son3c___1$","son4c___1$","son5c___1$",   
                         "son1c___2$","son2c___2$","son3c___2$","son4c___2$","son5c___2$",
                         "son1c___3$","son2c___3$","son3c___3$","son4c___3$","son5c___3$",
                         "son1c___996$","son2c___996$","son3c___996$","son4c___996$","son5c___996$",
                         "son1c___997$","son2c___997$","son3c___997$","son4c___997$","son5c___997$",
                         "son1c___998$","son2c___998$","son3c___998$","son4c___998$","son5c___998$",
                         "son1c_oth$","son2c_oth$","son3c_oth$","son4c_oth$","son5c_oth$",
                         "son1d$","son2d$","son3d$","son4d$","son5d$",
                         "son1e___1$","son2e___1$","son3e___1$","son4e___1$","son5e___1$",   
                         "son1e___2$","son2e___2$","son3e___2$","son4e___2$","son5e___2$",
                         "son1e___3$","son2e___3$","son3e___3$","son4e___3$","son5e___3$",
                         "son1e___4$","son2e___4$","son3e___4$","son4e___4$","son5e___4$",
                         "son1e___5$","son2e___5$","son3e___5$","son4e___5$","son5e___5$",
                         "son1e___996$","son2e___996$","son3e___996$","son4e___996$","son5e___996$",
                         "son1e___997$","son2e___997$","son3e___997$","son4e___997$","son5e___997$",
                         "son1e___998$","son2e___998$","son3e___998$","son4e___998$","son5e___998$",
                         "son1e_oth$","son2e_oth$","son3e_oth$","son4e_oth$","son5e_oth$",
                         "son1f$","son2f$","son3f$","son4f$","son5f",
                         "son1g$","son2g$","son3g$","son4g$","son5g$",
                         "son1h$","son2h$","son3h$","son4h$","son5h$",
                         "son1i$","son2i$","son3i$","son4i$","son5i$",
                         "son1j$","son2j$","son3j$","son4j$","son5j$",
                         "son1k$","son2k$","son3k$","son4k$","son5k$",
                         "son1l$","son2l$","son3l$","son4l$","son5l$",
                         "son1m$","son2m$","son3m$","son4m$","son5m$",
                         "son1n$","son2n$","son3n$","son4n$","son5n$"),
     value.name = c("sn1_name","sn2_name","sn3_name","sn4_name","sn5_name", 
                    "sn1_a","sn2_a","sn3_a","sn4_a","sn5_a",
                    "sn1_b","sn2_b","sn3_b","sn4_b","sn5_b",
                    "sn1_c_1","sn2_c_1","sn3_c_1","sn4_c_1","sn5_c_1",
                    "sn1_c_2","sn2_c_2","sn3_c_2","sn4_c_2","sn5_c_2",
                    "sn1_c_3","sn2_c_3","sn3_c_3","sn4_c_3","sn5_c_3",
                    "sn1_c_996","sn2_c_996","sn3_c_996","sn4_c_996","sn5_c_996",
                    "sn1_c_997","sn2_c_997","sn3_c_997","sn4_c_997","sn5_c_997",
                    "sn1_c_998","sn2_c_998","sn3_c_998","sn4_c_998","sn5_c_998",
                    "sn1_c_oth","sn2_c_oth","sn3_c_oth","sn4_c_oth","sn5_c_oth",
                    "sn1_d","sn2_d","sn3_d","sn4_d","sn5_d",
                    "sn1_e_1","sn2_e_1","sn3_e_1","sn4_e_1","sn5_e_1",
                    "sn1_e_2","sn2_e_2","sn3_e_2","sn4_e_2","sn5_e_2",
                    "sn1_e_3","sn2_e_3","sn3_e_3","sn4_e_3","sn5_e_3",
                    "sn1_e_4","sn2_e_4","sn3_e_4","sn4_e_4","sn5_e_4",
                    "sn1_e_5","sn2_e_5","sn3_e_5","sn4_e_5","sn5_e_5",
                    "sn1_e_996","sn2_e_996","sn3_e_996","sn4_e_996","sn5_e_996",
                    "sn1_e_997","sn2_e_997","sn3_e_997","sn4_e_997","sn5_e_997",
                    "sn1_e_998","sn2_e_998","sn3_e_998","sn4_e_998","sn5_e_998",
                    "sn1_e_oth","sn2_e_oth","sn3_e_oth","sn4_e_oth","sn5_e_oth",
                    "sn1_f","sn2_f","sn3_f","sn4_f","sn5_f",
                    "sn1_g","sn2_g","sn3_g","sn4_g","sn5_g",
                    "sn1_h","sn2_h","sn3_h","sn4_h","sn5_h",
                    "sn1_i","sn2_i","sn3_i","sn4_i","sn5_i",
                    "sn1_j","sn2_j","sn3_j","sn4_j","sn5_j",
                    "sn1_k","sn2_k","sn3_k","sn4_k","sn5_k",
                    "sn1_l","sn2_l","sn3_l","sn4_l","sn5_l",
                    "sn1_m","sn2_m","sn3_m","sn4_m","sn5_m",
                    "sn1_n","sn2_n","sn3_n","sn4_n","sn5_n"),
     variable.name = "Time")

sn <- melt(sn, id.vars = c("pid","Time"),
           measure.vars = patterns("name$", "_a$","_b$","_c_1$","_c_2$","_c_3$","_c_996$","_c_997$","_c_998$","_c_oth$",
                                   "_d$","_e_1$","_e_2$","_e_3$","_e_4$","_e_5$","_e_996$","_e_997$","_e_998$",
                                   "_e_oth$","_f$","_g$","_h$","_i$","_j$","_k$","_l$","_m$","_n$"),
           variable.name = "Person",
           value.name = c("sn_name", "sn_a","sn_b","sn_c_1","sn_c_2","sn_c_3","sn_c_996","sn_c_997","sn_c_998","sn_c_oth",
                    "sn_d","sn_e_1","sn_e_2","sn_e_3","sn_e_4","sn_e_5","sn_e_996","sn_e_997","sn_e_998",
                    "sn_e_oth","sn_f","sn_g","sn_h","sn_i","sn_j","sn_k","sn_l","sn_m","sn_n"))

sn[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

sn <- sn[!(sn_name == "998" | is.na(sn_name)),]

sn <- merge(sn, follow[,.(pid,Time)])

plev <- sn[, .(Npeople = factor(.N, levels=c("1","2","3","4","5")),
                  Any_HIV = any(sn_g == 1),
                  Any_CJI = any(sn_i == 1),
                  Any_ISU = any(sn_j == 1),
                  Any_SCH = any(sn_k == 1),
                  Any_WRK = any(sn_l == 1),
                  Any_PRT = any(sn_a %in% 
                                  c(1,2))), by = .(pid,Time)]

label(plev$Npeople) <- "Number of people listed"
label(plev$Any_HIV) <- "Any Network Members Diagnosed with HIV"
label(plev$Any_CJI) <- "Any Network Members with Criminal Justice System Involvement"
label(plev$Any_ISU) <- "Any Network Members with Illicit/Unprescribed Drug Use"
label(plev$Any_SCH) <- "Any Network Members in School"
label(plev$Any_WRK) <- "Any Network Members Working a Job on the Books"
label(plev$Any_PRT) <- "Any Network Members Who Are Romantic or Sex Partner"
```

### Participant Summaries

```{r}
table1(~ Npeople + Any_HIV + Any_CJI + Any_ISU +
         Any_SCH + Any_WRK + Any_PRT | Time, data = plev,
       overall = FALSE) |>
  t1flex()

```

### Network Member Summaries

```{r}
table1(~ sn_b + sn_c_1 + sn_c_2 + sn_c_3 + sn_f +
         sn_e_1 + sn_e_2 + sn_e_3 + sn_e_4 + sn_e_5 +
         sn_a + sn_d + sn_g +
         sn_h + sn_k + sn_l + sn_m + sn_n | Time, 
       data = as_factor(sn),
       overall = FALSE) |>
  t1flex()

```

## STI
```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for STI"

STI <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "sti\\d|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "sti\\d|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "sti\\d|pid"]))

STI <- melt(STI, id.vars = "pid",
            measure.vars = patterns("1a","1b","1c","1d","1e","1f","1g","1h","1i","1_oth",
                                    "2a","2b","2c","2d","2e","2f","2g","2h","2i"),
            variable.name = "Time",
            value.name = c("sti1a","sti1b","sti1c","sti1d","sti1e","sti1f","sti1g","sti1h","sti1i","sti1_oth",
                           "sti2a","sti2b","sti2c","sti2d","sti2e","sti2f","sti2g","sti2h","sti2i"))

STI[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

STI <- merge(STI, follow[,.(pid,Time)])
```

### Lifetime (Baseline)

```{r}
table1(~ sti1a + sti1b + sti1c + sti1d +
         sti1e + sti1f + sti1g + sti1h | Time, 
       data = as_factor(STI[Time == "BL"]), 
       overall = FALSE) |>
  t1flex()

```

### Past Year
```{r}
table1(~ sti2a + sti2b + sti2c + sti2d +
         sti2e + sti2f + sti2g + sti2h | Time, 
       data = as_factor(STI), 
       overall = FALSE) |>
  t1flex()

```

## WHO ASSIST

* WHO ASSIST Working Group (2002). The Alcohol, Smoking and Substance Involvement Screening Test (ASSIST): development, reliability and feasibility. _Addiction_, 97 (9): 1183-1194.

* Humeniuk RE, Ali RA, Babor TF, Farrell M, Formigoni ML, Jittiwutikarn J, Boerngen de Larcerda R, Ling W, Marsden J, Monteiro M, Nhiwhatiwa S, Pal H, Poznyak V & Simon S (2008). Validation of the Alcohol Smoking and Substance Involvement Screening Test (ASSIST). _Addiction_ 103(6): 1039-1047.

* Humeniuk RE, Henry-Edwards S, Ali RL, Poznyak V and Monteiro M (2010). _The Alcohol, Smoking and Substance Involvement Screening Test (ASSIST): manual for use in primary care_. Geneva, World Health Organization.

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for WHO ASSIST"

whoa <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "pid|whoassist[1-7][a-l]$"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "pid|whoassist[1-7][a-l]$"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "pid|whoassist[1-7][a-l]$"]))

whoa <- melt(whoa, id.vars = "pid",
             measure.vars = patterns("1a$","1b$","1c$","1d$","1e$","1f$","1g$","1h$","1i$","1j$","1k$","1l$",
                                     "2a$","2b$","2c$","2d$","2e$","2f$","2g$","2h$","2i$","2j$","2k$","2l$",
                                     "3a$","3b$","3c$","3d$","3e$","3f$","3g$","3h$","3i$","3j$","3k$","3l$",
                                     "4a$","4b$","4c$","4d$","4e$","4f$","4g$","4h$","4i$","4j$","4k$","4l$",
                                     "5a$","5b$","5c$","5d$","5e$","5f$","5g$","5h$","5i$","5j$","5k$","5l$",
                                     "6a$","6b$","6c$","6d$","6e$","6f$","6g$","6h$","6i$","6j$","6k$","6l$",
                                     "7a$","7b$","7c$","7d$","7e$","7f$","7g$","7h$","7i$","7j$","7k$","7l$"),
             variable.name = "Time",
             value.name = paste(rep(paste("Q", 1:7, sep=""), each = 12), letters[1:12], sep=""))

whoa <- melt(whoa, id.vars = c("pid","Time"),
           measure.vars = patterns("^Q1","^Q2","^Q3","^Q4","^Q5","^Q6","^Q7"),
           variable.name = "Substance",
     value.name = c("Q1","Q2","Q3","Q4","Q5","Q6","Q7"))

whoa[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

whoa[, Substance := car::recode(Substance, "1='tob';
                                            2='alc';
                                            3='can';
                                            4='coc';
                                            5='pstm';
                                            6='mthp';
                                            7='inh';
                                            8='sed';
                                            9='hal';
                                           10='popi';
                                           11='sopi';
                                           12='oth'", as.factor = TRUE,
                                     levels = c('tob','alc','can','coc','pstm','mthp','inh','sed','hal','popi','sopi','oth'))]

whoa <- merge(whoa, 
              na.omit(follow[,.(pid,Time)]))

whoa[Q1 == 0, Q2 := 1] # Recent use set to never if never used
whoa[Q1 == 0, Q6 := 1] # Concern set to never if never used
whoa[Q1 == 0, Q7 := 1] # Cut down set to never if never used
whoa[Q1 == 0 | Q2 == 1, Q3 := 1] # Urge set to never if no recent use
whoa[Q1 == 0 | Q2 == 1, Q4 := 1] # Problems set to never if no recent use
whoa[Q1 == 0 | Q2 == 1, Q5 := 1] # Failed set to never if no recent use
whoa[Substance == "tob", Q5 := 1] # Failed set to never for tobacco

whoa[, Use_P3M_num := case_when(
            Q2 == 1 ~ '0',
            Q2 == 2 ~ '2',
            Q2 == 3 ~ '3',
            Q2 == 4 ~ '4',
            Q2 == 5 ~ '6',
            is.na(Q2) ~ '0')]

whoa[, Urge_P3M_num := case_when(
            Q3 == 1 ~ '0',
            Q3 == 2 ~ '3',
            Q3 == 3 ~ '4',
            Q3 == 4 ~ '5',
            Q3 == 5 ~ '6',
            is.na(Q3) ~ '0')]

whoa[, Problems_P3M_num := case_when(
            Q4 == 1 ~ '0',
            Q4 == 2 ~ '4',
            Q4 == 3 ~ '5',
            Q4 == 4 ~ '6',
            Q4 == 5 ~ '7',
            is.na(Q4) ~ '0')]

whoa[, Failed_P3M_num := case_when(
        Substance == 'tob' ~ '0',
            Q5 == 1 & Substance != 'oth' ~ '0',
            Q5 == 2 & Substance != 'oth' ~ '5',
            Q5 == 3 & Substance != 'oth' ~ '6',
            Q5 == 4 & Substance != 'oth' ~ '7',
            Q5 == 5 & Substance != 'oth' ~ '8',
            Q5 == 1 & Substance == 'oth' ~ '0',
            Q5 == 2 & Substance == 'oth' ~ '4',
            Q5 == 3 & Substance == 'oth' ~ '5',
            Q5 == 4 & Substance == 'oth' ~ '6',
            Q5 == 5 & Substance == 'oth' ~ '7',
            is.na(Q5) ~ '0')]

whoa[, Concern_Ever_num := case_when(
            Use_P3M_num == 0 ~ '0',
            Q6 == 1 ~ '0',
            Q6 == 2 ~ '3',
            Q6 == 3 ~ '6',
            is.na(Q6) ~ '0')]

whoa[, Cut_Down_Ever_num := case_when(
            Use_P3M_num == 0 ~ '0',
            Q7 == 1 ~ '0',
            Q7 == 2 ~ '3',
            Q7 == 3 ~ '6',
            is.na(Q7) ~ '0')]

whoa[, Use_P3M_num := as.numeric(Use_P3M_num)]
whoa[, Urge_P3M_num := as.numeric(Urge_P3M_num)]
whoa[, Problems_P3M_num := as.numeric(Problems_P3M_num)]
whoa[, Failed_P3M_num := as.numeric(Failed_P3M_num)]
whoa[, Concern_Ever_num := as.numeric(Concern_Ever_num)]
whoa[, Cut_Down_Ever_num := as.numeric(Cut_Down_Ever_num)]

whoa[, Risk_Score := Use_P3M_num + Urge_P3M_num + Problems_P3M_num + 
       Failed_P3M_num + Concern_Ever_num + Cut_Down_Ever_num, 
     by = .(pid, Time, Substance)]

whoa[, Risk_Category := case_when(Risk_Score %in% 0:3 & Substance != 'alc' ~ 'Lower Risk',
                                    Risk_Score %in% 4:26 & Substance != 'alc' ~ 'Moderate Risk',
                                    Risk_Score > 26 & Substance != 'alc' ~ 'High Risk',
                                    Risk_Score %in% 0:10 & Substance == 'alc' ~ 'Lower Risk',
                                    Risk_Score %in% 11:26 & Substance == 'alc' ~ 'Moderate Risk',
                                    Risk_Score > 26 & Substance == 'alc' ~ 'High Risk'), by = .(pid, Substance)]

whoa[, Risk_Category := ordered(Risk_Category, levels = c('Lower Risk','Moderate Risk','High Risk'))]

whoa[, Not_Low_Risk := dplyr::case_when(Risk_Category == "Lower Risk" ~ "Lower Risk",
                                          Risk_Category != "Lower Risk" ~ "Moderate/High Risk")]

whoa[, Not_Low_Risk := factor(Not_Low_Risk, levels = c("Lower Risk","Moderate/High Risk"))]

assist_wide <- dcast(whoa[, .(pid, Time, Substance, Risk_Category, Risk_Score)],
                     pid + Time ~ Substance, value.var = c("Risk_Category","Risk_Score"))

label(assist_wide$Risk_Category_tob) <- " Tobacco products (cigarettes, chewing tobacco, cigars, etc.)"
label(assist_wide$Risk_Category_alc) <- "Alcoholic beverages (beer, wine, spirits, etc.)"
label(assist_wide$Risk_Category_can) <- "Marijuana (cannabis, pot, grass, hash, etc.)"
label(assist_wide$Risk_Category_coc) <- "Cocaine (coke, crack, etc.)"
label(assist_wide$Risk_Category_pstm) <- "Prescription stimulants (Ritalin, Concerta, Dexedrine, Adderall, diet pills, etc.)"
label(assist_wide$Risk_Category_mthp) <- "Methamphetamine (speed, crystal meth, ice, etc.)"
label(assist_wide$Risk_Category_inh) <- "Inhalants (poppers, nitrous, glue, gas, paint thinner, etc.)"
label(assist_wide$Risk_Category_sed) <- "Sedatives or Sleeping Pills (Valium, Ativan, Xanax, Klonopin, Librium, Rophynol, GHB, etc.)"
label(assist_wide$Risk_Category_hal) <- "Hallucinogens (Ecstasy, LSD, acid, mushrooms, PCP, Special K, etc.)"
label(assist_wide$Risk_Category_sopi) <- "Street opioids (heroin, opium, etc.)"
label(assist_wide$Risk_Category_popi) <- "Prescription opioids (morphine, codeine, fentanyl, oxycodone [Oxycontin, Percocet], hydrocodone [Vicodin], methadone, buprenorphine [Suboxone], etc.)"
label(assist_wide$Risk_Category_oth) <- "Other Drugs"

label(assist_wide$Risk_Score_tob) <- " Tobacco products (cigarettes, chewing tobacco, cigars, etc.)"
label(assist_wide$Risk_Score_alc) <- "Alcoholic beverages (beer, wine, spirits, etc.)"
label(assist_wide$Risk_Score_can) <- "Marijuana (cannabis, pot, grass, hash, etc.)"
label(assist_wide$Risk_Score_coc) <- "Cocaine (coke, crack, etc.)"
label(assist_wide$Risk_Score_pstm) <- "Prescription stimulants (Ritalin, Concerta, Dexedrine, Adderall, diet pills, etc.)"
label(assist_wide$Risk_Score_mthp) <- "Methamphetamine (speed, crystal meth, ice, etc.)"
label(assist_wide$Risk_Score_inh) <- "Inhalants (poppers, nitrous, glue, gas, paint thinner, etc.)"
label(assist_wide$Risk_Score_sed) <- "Sedatives or Sleeping Pills (Valium, Ativan, Xanax, Klonopin, Librium, Rophynol, GHB, etc.)"
label(assist_wide$Risk_Score_hal) <- "Hallucinogens (Ecstasy, LSD, acid, mushrooms, PCP, Special K, etc.)"
label(assist_wide$Risk_Score_sopi) <- "Street opioids (heroin, opium, etc.)"
label(assist_wide$Risk_Score_popi) <- "Prescription opioids (morphine, codeine, fentanyl, oxycodone [Oxycontin, Percocet], hydrocodone [Vicodin], methadone, buprenorphine [Suboxone], etc.)"
label(assist_wide$Risk_Score_oth) <- "Other Drugs"
```

### Risk Categories
```{r}
table1(~ . | Time, data = assist_wide[,.SD, .SDcols = names(assist_wide) %like% "Time|Category"], overall = FALSE) |>
  t1flex()

```

### Risk Scores
```{r}
table1(~ . | Time, data = assist_wide[,.SD, .SDcols = names(assist_wide) %like% "Time|Score"], overall = FALSE) |>
  t1flex()

```

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for three extra summaries from WHO ASSIST"

assist_wide <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE), 
                 list(assist_wide, 
                      whoa[, .(Mod_Hi_Risk = any(Risk_Category %in% c("Moderate Risk","High Risk"))), by = .(pid, Time)],
                      whoa[Substance != "tob", .(Mod_Hi_Risk_NoTOB = any(Risk_Category %in% c("Moderate Risk","High Risk"))), by = .(pid, Time)],
                      whoa[!(Substance %in% c("tob","can","alc")), .(Mod_Hi_Risk_NoTOBCANALC = any(Risk_Category %in% c("Moderate Risk","High Risk"))), by = .(pid, Time)]))

label(assist_wide$Mod_Hi_Risk) <- "Any Moderate or High Risk Substance Use"
label(assist_wide$Mod_Hi_Risk_NoTOB) <- "Any Moderate or High Risk Substance Use, Excluding Tobacco"
label(assist_wide$Mod_Hi_Risk_NoTOBCANALC) <- "Any Moderate or High Risk Substance Use, Excluding Tobacco, Alcohol, and Cannabis"
```

### Risk Scores Coefficient Alpha
```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for WHO ASSIST Cronbach's Alpha"

setDT(whoa)

whoa[,.(Alpha = round(ltm::cronbach.alpha(.SD)$alpha,2)), 
     .SDcols = names(whoa) %like% "num$", 
     by = .(Substance,Time)] |>
  dcast(Substance ~ Time, value.var = "Alpha") |>
  flextable::flextable()
```

## PrEP

```{r}
table1(~ bl_prep1 + bl_prep2,
       data = as_factor(blint[pid %in% Not_Withdrawn,])) |>
  t1flex()

```

## Substance Use and Mental Health Treatment

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for substance use and mental health treatment"

SUMH <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_sumhtx\\d+$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_sumhtx\\d+$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_sumhtx\\d+$|pid"]))

SUMH <- melt(SUMH, id.vars = "pid",
             measure.vars = patterns("tx1$","tx2$","tx3$","tx4$","tx5$",
                                     "tx6$","tx7$","tx8$","tx9$","tx10$",
                                     "tx11$","tx12$","tx13$","tx14$","tx15$",
                                     "tx16$","tx17$","tx18$","tx19$","tx20$",
                                     "tx21$","tx22$","tx23$","tx24$","tx25$",
                                     "tx26$","tx27$","tx28$","tx29$","tx30$"),
             variable.name = "Time",
             value.name = paste("sumhtx", 1:30, sep = ""))

SUMH[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

SUMH <- merge(follow[,.(pid,Time)], SUMH)
```

### Lifetime (Baseline)

```{r}
table1(~ sumhtx1 + sumhtx2 + sumhtx3 + sumhtx4 + sumhtx5 +
         sumhtx6 + sumhtx7 + sumhtx8 + sumhtx9 + sumhtx10 +
         sumhtx11 + sumhtx12 + sumhtx13 + sumhtx14 + sumhtx15, 
       data = as_factor(SUMH[Time == "BL",])) |>
  t1flex()

```

### Past Six Months

```{r}
table1(~ sumhtx16 + sumhtx17 + sumhtx18 + sumhtx19 + sumhtx20 +
         sumhtx21 + sumhtx22 + sumhtx23 + sumhtx24 + sumhtx25 +
         sumhtx26 + sumhtx27 + sumhtx28 + sumhtx29 + sumhtx30 | Time, 
       data = as_factor(SUMH),
       overall = FALSE) |>
  t1flex()

```

## PHQ

[Kroenke, K., Strine, T. W., Spitzer, R. L., Williams, J. B., Berry, J. T., & Mokdad, A. H. (2009). The PHQ-8 as a measure of current depression in the general population. Journal of affective disorders, 114(1-3), 163-173.](https://www.sciencedirect.com/science/article/pii/S0165032708002826)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for PHQ"

PHQ <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_phq\\d$|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_phq\\d$|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_phq\\d$|pid"]))

PHQ <- melt(PHQ, id.vars = "pid",
            measure.vars = patterns("phq1$","phq2$","phq3$","phq4$",
                                    "phq5$","phq6$","phq7$","phq8$"),
            variable.name = "Time",
            value.name = c("phq1","phq2","phq3","phq4",
                           "phq5","phq6","phq7","phq8"))

PHQ[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

PHQ <- merge(follow[,.(pid,Time)], PHQ)

phq_m <- melt(PHQ, id.vars = c("pid","Time"),
              measure.vars = patterns("^phq"),
              variable.name = "Item",
              value.name = "Response")

phq_m[, Response_n := ifelse(Response %in% 1:5, Response, as.integer(NA))]
phq_m[, NMISS := sum(is.na(Response_n)), by = .(pid,Time)]

PHQ <- merge(PHQ, 
             phq_m[,.(PHQTOTAL = if (all(NMISS > 3)) as.double(NA) else mean(Response_n - 1, na.rm = TRUE) * 8), 
                   by = .(pid,Time)],
             by = c("pid","Time"))

label(PHQ$PHQTOTAL) <- "PHQ Total Score"
```

```{r}
table1(~ . | Time, data = as_factor(PHQ[,.SD, .SDcols = names(PHQ) %like% "phq|PHQ|Time"]),
       overall = FALSE) |>
  t1flex()

```

<br> 

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(phq_m[Time == "BL",], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

## PTSD

[Cameron, R. P., & Gusman, D. (2003). The primary care PTSD screen (PC-PTSD): development and operating characteristics. Primary care psychiatry, 9(1), 9-14.](https://depts.washington.edu/fammed/improvingopioidcare/wp-content/uploads/sites/12/2018/02/Prins-2003.pdf)

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for PTSD"

PTSD <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_ptsd\\d$|ptsdscore|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_ptsd\\d$|ptsdscore|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_ptsd\\d|ptsdscore|pid"]))

PTSD <- melt(PTSD, id.vars = "pid",
            measure.vars = patterns("ptsd1$","ptsd2$","ptsd3$","ptsd4$",
                                    "score"),
            variable.name = "Time",
            value.name = c("ptsd1","ptsd2","ptsd3","ptsd4",
                           "ptsdscore"))

PTSD[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

PTSD <- merge(follow[,.(pid,Time)], PTSD)
```

```{r}
table1(~ . | Time, data = as_factor(PTSD[,.SD, .SDcols = names(PTSD) %like% "ptsd|score|Time"]),
       overall = FALSE) |>
  t1flex()

```

## Resilience

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for resilience"

Resil <- Reduce(function(x, y) merge(x, y, intersect(names(x), names(y)), all = TRUE),
       list(blint[pid %in% Not_Withdrawn,.SD, .SDcols = names(blint) %like% "_resilience\\d|pid"], 
            f1int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f1int) %like% "_resilience\\d|pid"],
            f2int[pid %in% Not_Withdrawn,.SD, .SDcols = names(f2int) %like% "_resilience\\d|pid"]))

Resil <- melt(Resil, id.vars = "pid",
               measure.vars = patterns("resilience1$","resilience2$","resilience3$","resilience4$","resilience5$",
                                       "resilience6$","resilience7$","resilience8$","resilience9$","resilience10$"),
               variable.name = "Time",
               value.name = paste("resilience", 1:10, sep = ""))

Resil[, Time := car::recode(Time, "1='BL';2='9M';3='18M'", as.factor = TRUE, levels = c('BL','9M','18M'))]

Resil <- merge(follow[,.(pid,Time)], Resil)

Resil_m <- melt(Resil, id.vars = c("pid","Time"),
                 variable.name = "Item", value.name = "Response")

Resil_m[, Response_n := ifelse(Response %in% 1:5, Response - 1, as.integer(NA))]

Resil <- merge(Resil,
      Resil_m[, .(Resilience = mean(Response_n, na.rm = TRUE)*10), by = .(pid,Time)],
      by = c("pid","Time"))

label(Resil$Resilience) <- "Resilience Total Score"
```

```{r}
table1(~ . | Time, data = as_factor(Resil[, .SD, .SDcols = names(Resil) %like% "resilience\\d$|Resil|Time"]),
       overall = FALSE) |>
  t1flex()

```

<br>

Coefficient Alpha (Baseline)

```{r}
myalpha <- dcast(Resil_m[Time == "BL",.(pid,Item,Response_n)], pid ~ Item, value.var = "Response_n") %>%
  .[, pid := NULL] |>
  psych::alpha()

myalpha[1:4] |> pander()
```

# SU Screening

```{r}
setDT(drug_test_form)

drug_test_form[, Time := car::recode(redcap_event, "'baseline_interview'='BL';
                                                    'follow_up_1_interv'='9M';
                                                    'follow_up_2_interv'='18M'", as.factor = TRUE,
                                     levels = c("BL","9M","18M"))]


table1(~ . | Time , data = as_factor(drug_test_form[pid %in% Not_Withdrawn, 
                                  .SD, .SDcols = names(drug_test_form) %like% "^drug_sample1_test|drug_accept_test|Time"]),
       render = my.render,
       overall = FALSE) |>
  t1flex()

```

# EMA

## Timing of EMA Bursts 1-8

-   The earliest **first** burst of EMA began on `r format(min(ema_burst_1_form$ema_start_w1, na.rm=TRUE), "%A, %B %d, %Y")`
-   The earliest **second** burst of EMA began on `r format(min(ema_burst_2_form$ema_start_w2, na.rm=TRUE), "%A, %B %d, %Y")`
-   The earliest **third** burst of EMA began on `r format(min(ema_burst_3_form$ema_start_w3, na.rm=TRUE), "%A, %B %d, %Y")`
-   The earliest **fourth** burst of EMA began on `r format(min(ema_burst_4_form$ema_start_w4, na.rm=TRUE), "%A, %B %d, %Y")`
-   The earliest **fifth** burst of EMA began on `r format(min(ema_burst_5_form$ema_start_w5, na.rm=TRUE), "%A, %B %d, %Y")`
-   The earliest **sixth** burst of EMA began on `r format(min(ema_burst_6_form$ema_start_w6, na.rm=TRUE), "%A, %B %d, %Y")`
-   The earliest **seventh** burst of EMA began on `r format(min(ema_burst_7_form$ema_start_w7, na.rm=TRUE), "%A, %B %d, %Y")`
-   The earliest **eighth** burst of EMA began on `r format(min(ema_burst_8_form$ema_start_w8, na.rm=TRUE), "%A, %B %d, %Y")`

## Item Summaries

### Daily

```{r}
table1(~ v1_ema_q1 + v1_ema_q2___1 + v1_ema_q2___2 + v1_ema_q2___3 +
         v1_ema_q2___4 + v1_ema_q2___5 + v1_ema_q2___6 + v1_ema_q2___7 +
         v1_ema_q2___8 + v1_ema_q2___9 + v1_ema_q2___10 + v1_ema_q2___11 +
         v1_ema_q2___996 + v1_ema_q3 + v1_ema_q4 + v1_ema_q5 + v1_ema_q6, 
       data = as_factor(ema_daily_assessment)) |>
  t1flex()

```

### End of the Day

```{r}
table1(~ v1_ema4_q1 + v1_ema4_q3 + v1_ema4_q4 + v1_ema4_q5 + v1_ema4_q6 + v1_ema4_q7 +
                           v1_ema4_q2___1 + v1_ema4_q2___2 + v1_ema4_q2___3 + v1_ema4_q2___4 +
                             v1_ema4_q2___5 + v1_ema4_q2___6 + v1_ema4_q2___7 + v1_ema4_q2___8 +
                             v1_ema4_q2___9 + v1_ema4_q2___10 + v1_ema4_q2___11 + v1_ema4_q2___996, 
       data = as_factor(ema_end_of_day_assessment)) |>
  t1flex()

```

<br>

```{r, echo=TRUE}
#| code-fold: true
#| code-summary: "Show the code for integrating items related to daily medication adherence"

setDT(ema_end_of_day_assessment)

ema_end_of_day_assessment[is.na(v1_ema4_q9_v2) & !is.na(v1_ema4_q7) & v1_ema4_q7 == 0, v1_ema4_q9_v2 := 0]
ema_end_of_day_assessment[is.na(v1_ema4_q9) & !is.na(v1_ema4_q7) & v1_ema4_q7 == 0, v1_ema4_q9 := 0]
ema_end_of_day_assessment[is.na(v1_ema4_q9_v2) & v1_ema4_q9 == 0, v1_ema4_q9_v2 := 0]

ema_end_of_day_assessment[is.na(v1_ema4_q9_v2) & v1_ema4_q9 == 10, v1_ema4_q9_v2 := 3]
ema_end_of_day_assessment[is.na(v1_ema4_q9) & v1_ema4_q9_v2 == 3, v1_ema4_q9 := 10]
ema_end_of_day_assessment[is.na(v1_ema4_q9_v2) & v1_ema4_q9 %in% 2:9, v1_ema4_q9_v2 := 1]

ema_end_of_day_assessment$v1_ema4_q9_v2 <- labelled(
  ema_end_of_day_assessment$v1_ema4_q9_v2,
  c("None of my doses" = 0, "Some of my dosees" = 1, "Most of my doses" = 2, "All of my HIV medication doses" = 3)
)

var_label(ema_end_of_day_assessment$v1_ema4_q9_v2) <- "How much of your HIV medication did you take today?"
```

```{r}
table1(~ v1_ema4_q9 + v1_ema4_q9_v2 + v1_ema4_q7, 
       data = as_factor(ema_end_of_day_assessment[!is.na(v1_ema4_q7) | !is.na(v1_ema4_q9) | !is.na(v1_ema4_q9_v2)])) |>
  t1flex()

```

<br>

#### What are the main reasons you did not take HIV medication today?

```{r}
table1(~ ., data = as_factor(ema_end_of_day_assessment[v1_ema4_q7 == 0 | v1_ema4_q9_v2 == 0, 
                                                       .SD, .SDcols = names(ema_end_of_day_assessment) %like% "^v1_ema4_q8___"])) |>
  t1flex()

```

<br>

# Suppressed Viral Load Over Time

```{r}
setDT(blood_draw_form)

long_VL <- blood_draw_form[pid %in% Not_Withdrawn,.(pid,redcap_event,blood_vl_q2,blood_vl_q3,blood_vl_q4)]

wide_VL <- dcast(long_VL[!is.na(blood_vl_q2),.(pid,redcap_event,blood_vl_q2)],
      pid ~ redcap_event, value.var = "blood_vl_q2")

setnames(wide_VL, old = c("baseline_interview", 
                          "follow_up_1_interv", 
                          "follow_up_2_interv"),
                  new = c('BL_Undetectable',
                          'FU1_Undetectable',
                          'FU2_Undetectable'))
```

## Viral Load $\lt$ 200 copies/mL at Baseline (n=219)

```{r}
gtsummary::tbl_cross(as_factor(wide_VL[pid %in% Not_Withdrawn & 
                                       !is.na(BL_Undetectable) &
                                       BL_Undetectable == 1,]), 
                               row = FU1_Undetectable, 
                               col = FU2_Undetectable,
                               percent = "cell",
                               label = list(FU1_Undetectable ~ "Suppressed at 9M", 
                                            FU2_Undetectable ~ "Suppressed at 18M")) |>
gtsummary::as_flex_table()
```

## Viral Load $\ge$ 200 copies/mL at Baseline (n=52)

```{r}
gtsummary::tbl_cross(as_factor(wide_VL[pid %in% Not_Withdrawn & 
                                       !is.na(BL_Undetectable) &
                                       BL_Undetectable == 0,]), 
                               row = FU1_Undetectable, 
                               col = FU2_Undetectable,
                               percent = "cell",
                               label = list(FU1_Undetectable ~ "Suppressed at 9M", 
                                            FU2_Undetectable ~ "Suppressed at 18M")) |>
gtsummary::as_flex_table()
```

```{r}
change_VL_status <- wide_VL[pid %in% Not_Withdrawn &
        (!is.na(FU1_Undetectable) & FU1_Undetectable != BL_Undetectable) |
        (!is.na(FU2_Undetectable) & FU2_Undetectable != BL_Undetectable) |
        (!is.na(FU1_Undetectable) & !is.na(FU2_Undetectable) & FU1_Undetectable != FU2_Undetectable),]
```

```{r}
longit_cohort <- wide_VL[pid %in% Not_Withdrawn] |> 
  cohort_start("Enrolled<br>") |>
    cohort_define(
    bl_n = .full |> filter(BL_Undetectable == 0),
    bl_y = .full |> filter(BL_Undetectable == 1),
    bl_n_f1_n = bl_n |> filter(FU1_Undetectable == 0),
    bl_n_f1_y = bl_n |> filter(FU1_Undetectable == 1),
    bl_y_f1_n = bl_y |> filter(FU1_Undetectable == 0),
    bl_y_f1_y = bl_y |> filter(FU1_Undetectable == 1),
    bl_n_f1_n_f2_n = bl_n_f1_n |> filter(FU2_Undetectable == 0),
    bl_n_f1_y_f2_n = bl_n_f1_y |> filter(FU2_Undetectable == 0),
    bl_y_f1_n_f2_n = bl_y_f1_n |> filter(FU2_Undetectable == 0),
    bl_y_f1_y_f2_n = bl_y_f1_y |> filter(FU2_Undetectable == 0),
    bl_n_f1_n_f2_y = bl_n_f1_n |> filter(FU2_Undetectable == 1),
    bl_n_f1_y_f2_y = bl_n_f1_y |> filter(FU2_Undetectable == 1),
    bl_y_f1_n_f2_y = bl_y_f1_n |> filter(FU2_Undetectable == 1),
    bl_y_f1_y_f2_y = bl_y_f1_y |> filter(FU2_Undetectable == 1)
    ) |>
  cohort_label(
    bl_n = "Unsuppressed<br>at BL<br>",
    bl_y = "Suppressed<br>at BL<br>",
    bl_n_f1_n = "Unsuppressed<br>at 9M<br>",
    bl_n_f1_y = "Suppressed<br>at 9M<br>",
    bl_y_f1_n = "Unsuppressed<br>at 9M<br>",
    bl_y_f1_y = "Suppressed<br>at 9M<br>",
    bl_n_f1_n_f2_n = "Unsuppressed<br>at 18M<br>",
    bl_n_f1_y_f2_n = "Unsuppressed<br>at 18M<br>",
    bl_y_f1_n_f2_n = "Unsuppressed<br>at 18M<br>",
    bl_y_f1_y_f2_n = "Unsuppressed<br>at 18M<br>",
    bl_n_f1_n_f2_y = "Suppressed<br>at 18M<br>",
    bl_n_f1_y_f2_y = "Suppressed<br>at 18M<br>",
    bl_y_f1_n_f2_y = "Suppressed<br>at 18M<br>",
    bl_y_f1_y_f2_y = "Suppressed<br>at 18M<br>")
```

```{r}
longit_flow <- longit_cohort |>
  consort_box_add("NBL", 21.42857, 20, cohort_count_adorn(longit_cohort, bl_n)) |>
  consort_box_add("YBL", 78.57143, 20, cohort_count_adorn(longit_cohort, bl_y)) |>
  consort_box_add("NBLNF1",  7.143, 10, cohort_count_adorn(longit_cohort, bl_n_f1_n)) |>  
  consort_box_add("NBLYF1",  35.714, 10, cohort_count_adorn(longit_cohort, bl_n_f1_y)) |>  
  consort_box_add("YBLNF1",  64.286, 10, cohort_count_adorn(longit_cohort, bl_y_f1_n)) |>
  consort_box_add("YBLYF1",  92.857, 10, cohort_count_adorn(longit_cohort, bl_y_f1_y)) |>    
  consort_box_add("NBLNF1NF2",      0, 0, cohort_count_adorn(longit_cohort, bl_n_f1_n_f2_n)) |>
  consort_box_add("NBLNF1YF2",   14.3, 0, cohort_count_adorn(longit_cohort, bl_n_f1_n_f2_y)) |>    
  consort_box_add("NBLYF1NF2",   28.6, 0, cohort_count_adorn(longit_cohort, bl_n_f1_y_f2_n)) |>    
  consort_box_add("NBLYF1YF2",   42.9, 0, cohort_count_adorn(longit_cohort, bl_n_f1_y_f2_y)) |>    
  consort_box_add("YBLNF1NF2",   57.1, 0, cohort_count_adorn(longit_cohort, bl_y_f1_n_f2_n)) |>    
  consort_box_add("YBLNF1YF2",   71.4, 0, cohort_count_adorn(longit_cohort, bl_y_f1_n_f2_y)) |>    
  consort_box_add("YBLYF1NF2",   85.7, 0, cohort_count_adorn(longit_cohort, bl_y_f1_y_f2_n)) |>
  consort_box_add("YBLYF1YF2",    100, 0, cohort_count_adorn(longit_cohort, bl_y_f1_y_f2_y)) |>
  consort_arrow_add(start = "NBL", end = "NBLNF1", end_side = "top") |>
  consort_arrow_add(start = "NBL", end = "NBLYF1", end_side = "top") |>
  consort_arrow_add(start = "YBL", end = "YBLNF1", end_side = "top") |>
  consort_arrow_add(start = "YBL", end = "YBLYF1", end_side = "top") |>
  consort_arrow_add(start = "NBLNF1", end = "NBLNF1NF2", end_side = "top") |>
  consort_arrow_add(start = "NBLNF1", end = "NBLNF1YF2", end_side = "top") |>
  consort_arrow_add(start = "NBLYF1", end = "NBLYF1NF2", end_side = "top") |>
  consort_arrow_add(start = "NBLYF1", end = "NBLYF1YF2", end_side = "top") |>
  consort_arrow_add(start = "YBLNF1", end = "YBLNF1NF2", end_side = "top") |>
  consort_arrow_add(start = "YBLNF1", end = "YBLNF1YF2", end_side = "top") |>
  consort_arrow_add(start = "YBLYF1", end = "YBLYF1NF2", end_side = "top") |>
  consort_arrow_add(start = "YBLYF1", end = "YBLYF1YF2", end_side = "top")

```

```{r, include = TRUE, fig.width = 11, fig.height = 3, dev='svg'}
longit_flow |>
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = 4, margin_v = 4)
```

```{r, eval=FALSE}
consort_plot(wide_VL[pid %in% Not_Withdrawn],
             orders = c(pid      = 'Enrolled',
                        BL_Undetectable = 'Undetectable BL',
                        FU1_Undetectable = 'Undetectable 9M',
                        FU2_Undetectable = 'Undetectable 18M'),
             allocation = 'BL_Undetectable',
             side_box = c('FU1_Undetectable'))
```

```{r}
library(gtsummary)

wide_VL[, BL_Undetectable := dplyr::case_when(BL_Undetectable == 1 ~ "Suppressed at BL (n=222)",
                                              BL_Undetectable == 0 ~ "Not Suppressed at BL (n=52)")]

wide_VL[, FU1_Undetectable := dplyr::case_when(FU1_Undetectable == 1 ~ "Suppressed at 9M",
                                               FU1_Undetectable == 0 ~ "Not Suppressed at 9M")]

wide_VL[, FU2_Undetectable := dplyr::case_when(FU2_Undetectable == 1 ~ "Suppressed at 18M",
                                               FU2_Undetectable == 0 ~ "Not Suppressed at 18M")]
```

```{r, results='asis', eval=FALSE}
mytab4 <- wide_VL[pid %in% Not_Withdrawn,] |> 
  tbl_strata(
    strata = BL_Undetectable,
    .tbl_fun =
      ~ .x |>
      tbl_cross(FU1_Undetectable, FU2_Undetectable, margin = NULL,
                percent = "cell",
                label = list(FU1_Undetectable ~ "9 Month Follow-Up",
                             FU2_Undetectable ~ "18 Month Follow-Up")) 
  )

print(mytab4)
```

-   n=`r nrow(change_VL_status)` participants had a change in HIV viral load suppression over time
    -   n=`r nrow(change_VL_status[BL_Undetectable == 1,])` participants who were enrolled with $\lt$ 200 copies/mL became unsuppressed
    -   n=`r nrow(change_VL_status[BL_Undetectable == 0,])` participants who were enrolled with $\ge$ 200 copies/mL became suppressed

```{r, echo=FALSE, include=FALSE}
pscrn_meta <- REDCapR::redcap_metadata_read(redcap_uri = uri, token=tkns[3,2])

pscrn_meta[["data"]] |> subset(, select = "form_name") |> unique() |> as.vector()

N4_pscrn_stbl <- read_redcap(redcap_uri=uri, forms = c("public_contact_form","follow_up_tracker" ), 
                       raw_or_label = "raw", token=tkns[3,2],
                       allow_mixed_structure = TRUE)

N4_pscrn_stbl |>
  make_labelled() |>
bind_tibbles(tbls = c("public_contact_form",
                      "follow_up_tracker"))
```

# Prescreening Form (n=`r nrow(follow_up_tracker)`)

-   Prescreener completed (n=`r sum(follow_up_tracker$fu_form3___1 == 1)`)\
-   Refused prescreener (n=`r sum(follow_up_tracker$fu_form3___2 == 1)`)\
-   Recruiter only (n=`r sum(follow_up_tracker$fu_form3___3 == 1)`)\
-   Needs additional contact info (n=`r sum(follow_up_tracker$fu_form3___4 == 1)`)\
-   Do not contact (n=`r sum(follow_up_tracker$fu_form3___5 == 1)`)

```{r}
setDT(blood_draw_form)

blood_draw_form[, Time := car::recode(redcap_event, "'baseline_interview'='BL';
                                                    'follow_up_1_interv'='9M';
                                                    'follow_up_2_interv'='18M'", as.factor = TRUE,
                                     levels = c("BL","9M","18M"))]
```

```{r}
label(assist_wide$Risk_Category_tob) <- "Tobacco products (cigarettes, chewing tobacco, cigars, etc.)"
label(assist_wide$Risk_Category_alc) <- "Alcoholic beverages (beer, wine, spirits, etc.)"
label(assist_wide$Risk_Category_can) <- "Marijuana (cannabis, pot, grass, hash, etc.)"
label(assist_wide$Risk_Category_coc) <- "Cocaine (coke, crack, etc.)"
label(assist_wide$Risk_Category_pstm) <- "Prescription stimulants (Ritalin, Concerta, Dexedrine, Adderall, diet pills, etc.)"
label(assist_wide$Risk_Category_mthp) <- "Methamphetamine (speed, crystal meth, ice, etc.)"
label(assist_wide$Risk_Category_inh) <- "Inhalants (poppers, nitrous, glue, gas, paint thinner, etc.)"
label(assist_wide$Risk_Category_sed) <- "Sedatives or Sleeping Pills (Valium, Ativan, Xanax, Klonopin, Librium, Rophynol, GHB, etc.)"
label(assist_wide$Risk_Category_hal) <- "Hallucinogens (Ecstasy, LSD, acid, mushrooms, PCP, Special K, etc.)"
label(assist_wide$Risk_Category_sopi) <- "Street opioids (heroin, opium, etc.)"
label(assist_wide$Risk_Category_popi) <- "Prescription opioids (morphine, codeine, fentanyl, oxycodone [Oxycontin, Percocet], hydrocodone [Vicodin], methadone, buprenorphine [Suboxone], etc.)"
label(assist_wide$Risk_Category_oth) <- "Other Drugs"

label(assist_wide$Risk_Score_tob) <- "Tobacco products (cigarettes, chewing tobacco, cigars, etc.)"
label(assist_wide$Risk_Score_alc) <- "Alcoholic beverages (beer, wine, spirits, etc.)"
label(assist_wide$Risk_Score_can) <- "Marijuana (cannabis, pot, grass, hash, etc.)"
label(assist_wide$Risk_Score_coc) <- "Cocaine (coke, crack, etc.)"
label(assist_wide$Risk_Score_pstm) <- "Prescription stimulants (Ritalin, Concerta, Dexedrine, Adderall, diet pills, etc.)"
label(assist_wide$Risk_Score_mthp) <- "Methamphetamine (speed, crystal meth, ice, etc.)"
label(assist_wide$Risk_Score_inh) <- "Inhalants (poppers, nitrous, glue, gas, paint thinner, etc.)"
label(assist_wide$Risk_Score_sed) <- "Sedatives or Sleeping Pills (Valium, Ativan, Xanax, Klonopin, Librium, Rophynol, GHB, etc.)"
label(assist_wide$Risk_Score_hal) <- "Hallucinogens (Ecstasy, LSD, acid, mushrooms, PCP, Special K, etc.)"
label(assist_wide$Risk_Score_sopi) <- "Street opioids (heroin, opium, etc.)"
label(assist_wide$Risk_Score_popi) <- "Prescription opioids (morphine, codeine, fentanyl, oxycodone [Oxycontin, Percocet], hydrocodone [Vicodin], methadone, buprenorphine [Suboxone], etc.)"
label(assist_wide$Risk_Score_oth) <- "Other Drugs"
```

```{r}
Spanish_Activities <- subset(locator_form, pid %in% Not_Withdrawn, select = c(pid,loc_language))
setDT(Spanish_Activities)
```

```{r}
save(list = c(setdiff(ls(), c("tkns","token","plist","figtop","figtop_VL","i",
                "myalpha","mytab1","mytab2","mytab3","mytab4","mytab9",
                "uri","rcon","baseline_consent_form","Cohort_DT","fu1_referral_form_staff",
                "lab_upload_form","locator_form","N4_bl_stbl","N4_blood_stbl","N4_drug_stbl",
                "N4_ema_stbl","N4_fu1_stbl","N4_fu2_stbl","N4_loc_stbl","N4_other_stbl",
                "N4_screen_stbl","zoom_tracker_form","referral_form","practice_ema"))),
     file = "c:/chuck/NYU/Gwadz/Adolescent Longitudinal/N4R/n4c-Tidy.Rdata")
```



